% ---------------------------------------------------------------------
% Growlrr Foods -- CatPro v5 Premix (100 g packet) -- Rev H.3.0.0
% All weights in g per 100 g packet. Carrier q.s. to 100 g.
% ---------------------------------------------------------------------

\subsection*{CatPro v5 Premix (100 g packet per 10Kg Retort Run) RED Sticker}
\addcontentsline{toc}{subsection}{CatPro v5 Premix (100 g packet)}
\vspace{0.5em}
\noindent\textit{All weights are expressed in grams (g) per 100 g premix formulation. Carrier (q.s.) to reach 100 g}
\vspace{0.5em}


\begin{longtable}{@{}p{6.0cm}r@{\hspace{1em}}p{5.0cm}@{}}
\caption{Catpro Premix Composition (per 100 g premix)}\\
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Function / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Function / Notes} \\
\midrule
\endhead

Choline chloride (60\% assay)                         & 32.00000  & Primary methyl donor and carrier base \\[2pt]
Taurine                                               & 15.00000  & Essential amino sulphonate for cats; heat-labile overage included \\[2pt]
Magnesium gluconate (USP grade)                       & 10.00000  & Primary  chelator; provides stable Mg source \\[2pt]  
L-Carnitine (as L-carnitine tartrate )                & 9.000000  & Supports fat metabolism, essential with cooked meat and oil fishes \\[2pt]
Inulin (chicory root powder, FOS)                     & 8.000000  & Prebiotic fibre; improves gut flora stability and stool quality \\[2pt]
Betaine (Trimethylglycine)                            & 6.000000  & Hepatic methyl donor and osmolyte; supports liver fat metabolism and hydration balance \\[2pt] 
Potassium Citrate (Tripotassium citrate, food grade)  & 5.000000  & Secondary chelator; critical for cat urinary health reducing struvite crystal risk\\[2pt]
DL-Methionine (USP grade)                             & 3.500000  & Urinary health support; maintains healthy urine pH; Sulfur for protein metabolism \\[2pt]
Ascorbic acid (fine powder)                           & 2.000000  & Antioxidant cofactor for metal complex stability \\[2pt] 
Vitamin K$_2$ (Menaquinone--7, 1\% assay)             & 1.700000  & Provides $\approx$17\,\textmu g MK-7 per pouch; aids calcium utilization and bone health \\[2pt]
L-Cysteine (USP grade)                                & 1.500000  & Complements DL--methionine to balance sulfur amino acids and strengthen coat/keratin \\[2pt]
Zinc bisglycinate chelate (25\% Zn)                   & 1.100000  & Chelated zinc to meet AAFCO limits \\[2pt]
Calcium pantothenate (Vitamin B$_5$)                  & 0.800000  & Coenzyme---A precursor; supports fatty--acid metabolism and adrenal function \\[2pt]
Iron proteinate (20\% Fe)                             & 0.750000  & Chelated iron to meet target  \\[2pt]
Selenium yeast (0.20\% Se)                            & 0.550000  & (delivers target $\approx$ 11 \textmu g selenium per 100g wet food pouch) \\[2pt]
Niacin (B$_3$)                                        & 0.250000  & Metabolic cofactor \\[2pt]
Copper proteinate (10\% Cu)                           & 0.300000  & Trace mineral meets requirements \\[2pt]
Thiamine (B$_1$)                                      & 0.190000  & Hightly heat-labile B vitamin; ample overage applied  \\[2pt]
Manganese proteinate (10\% Mn)                        & 0.150000  & Trace mineral  meets requirements \\[2pt]
Riboflavin (B$_2$)                                    & 0.050000  & Energy cofactor  \\[2pt]
Pyridoxine (B$_6$)                                    & 0.050000  & Amino-acid metabolism cofactor \\[2pt]  
Vitamin D$_3$ (cholecalciferol, 100000 IU g$^{-1}$)   & 0.035000  & (provides approximately 35 IU per 100 g wet food pouch)\\[2pt]
Vitamin A (retinyl palmitate, 320000 IU g$^{-1}$)     & 0.015000  & (provides approximately 50 IU per 100 g wet food pouch) \\[2pt]
Potassium iodate (KIO$_3$) & 0.010000 & $\approx$ 60 $\mu$g Iodine per 100g wet food pouch. Sardine SKU provides additional $\approx$ 20 $\mu$g  \cite{sardinecap}\\[2pt]
Biotin (Vitamin B7), Pharma Grade D-Biotin            & 0.008000  & Skin/coat support; very low inclusion, provides 80$\mu$g biotin per 100g wet food pouch \\[2pt]
\midrule
Mixed tocopherols (($\alpha:\beta:\gamma:\delta$) =1.0:0.3:6.0:2.0 50\% active powder) & 1.000000  & Antioxidant for premix shelf-life stability (not primary source of dietary vitamin E) \\[2pt]
\midrule
Anti-caking carrier (q.s)                             & 1.042000  & q.s to 100.000000 g per premix packet \\[2pt]

\midrule
\textbf{Total}                                         & \textbf{100.000000} & Use one 100 packet per 10 kg run. MOQ 10 Packets. \\
\bottomrule
\end{longtable}
% ------------------- NOTES -------------------
\vspace{1em}

\subsection*{Composition for CatCorePro}

\begin{table}[h]
\centering
\caption{CatCorePro Composition per 10 kg run (or 100 pouches)}
\label{tab:catcorepro_composition_}
\begin{tabular}{@{}l r r@{}}
\toprule
\textbf{Component} & \textbf{Dose per 10 kg} & \textbf{Per pouch} \\
\midrule
CatCore Fresh Meat Protiens & 6500g & 65.0g \\ [3pt]
Omega-3 Fish Oil PV<=5.0meq/Kg & 250ml & 2.50ml \\[3pt]
CatPro Premix & 100 g & 1.0 g \\[3pt]
Mixed tocopherol liquid premix & 100 ml & 1.0 ml \\[3pt]
Palatant Liquid Premix & 100ml & 1.0ml \\[3pt]
Alginate gel - Ca Premix & 100g & 1.0g \\[3pt]
\midrule
Rendered Bone Broth & 4150g & 41.5g \\[3pt]
\midrule
Nett Weight per pouch & 112.5g pre-retort & 101.5g $\pm$0.50; declared weight 100.00g\\[3pt]
\bottomrule
\end{tabular}
\end{table}

\noindent\textbf{Composition Notes:}
\begin{itemize}
\item\itembf {CatCore: }Provides high quality muscle, organ, skeletal and fish meat protiens. Primary source of protiens, fats, vitamins, minerals. 
\item \textbf{Catcore Useage: }6.5 Kg Fresh meat blends per 10 kg production run of CatCore or 65.0 g per 100 g wet food pouch.
\item \textbf{CatPro Premix: } Complements CatCore Protein-Ca Premix with complete essential vitamins, minerals and chelators and adequate retort loss overage. 
\item\textbf{AAFCO Compliance: } Together CatCore and CatPro meets AAFCO requirements for complete and balanced nutrition when paired per diet chart. 
\item\textbf{Design Overages: }Enhanced taurine formulation for cardiac health support. Vitamin A is balanced carefully with daily 4.0g fresh liver from 2 CatCore pouches to avoid stacking. Ca:P >=1.1:1 within AAFCO recommended limits when paired  as per diet chart. 
\item \textbf{Antioxidant Premix: } Provides Primary Vitamin E (dl-$\alpha$tocopheryl) and mixed antioxidants for enhanced oxidative stability.
\item \textbf{Alginate Gel - Ca Premix:} Alginate gel forms cross-link chain with Calcium under retort heat. Source of 80mg dietary calcium per 100g wet food. Maintains Ca:P ratio. 
\item \textbf{Omega-3 Fish Oil Blend:} Provides functional Omega-3:Omega-6 fatty acids balance. 
\item \textbf{Palatant Premix: } Meat Hydrolysants for palatability.
\item\item{Rendered Bone Broth: } Solvent base for retort processing; improves hydration, adds collagen, chondoitin and other bone joint stability nutrients. 
\end{itemize}



