% ---------------------------------------------------------------------
% Growlrr Foods -- DogPro v5 Premix (100 g packet) -- Rev H.3.1.0
% All weights in g per 100 g packet. Rebalanced for enhanced taurine
% ---------------------------------------------------------------------

\subsection*{DogPro v5 Premix (100 g packet per 10 kg retort run)}
\noindent\textit{All weights are expressed in grams (g) per 100 g premix formulation. Carrier (q.s.) to reach 100 g.}
\begin{longtable}{@{}p{6.0cm}r@{\hspace{1em}}p{5.0cm}@{}}
\caption{DogPro v5 Premix Composition (per 100 g premix)}\\
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Function / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Function / Notes} \\
\midrule
\endhead

\subsection*{DogPro v5 Premix (100 g packet per 10 kg retort run) — FINAL}
\noindent\textit{All weights are expressed in grams (g) per 100 g premix formulation. Carrier (q.s.) to reach 100 g.}
\begin{longtable}{@{}p{6.0cm}r@{\hspace{1em}}p{5.0cm}@{}}
\caption{DogPro v5 Premix Composition (per 100 g premix)}\\
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Function / Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Function / Notes} \\
\midrule
\endhead

Choline chloride (60\% assay)                       & 20.000000 & Primary methyl donor and carrier base \\[2pt]
Taurine (≥ 99\%)                                    & 10.000000 & Essential sulphonic amino acid; margin for breed/diet variability \\[2pt]
Inulin (chicory root powder, FOS)                   & 12.000000 & Prebiotic fibre; gut flora stability and stool quality \\[2pt]
Magnesium gluconate (USP grade)                     & 10.000000 & Secondary chelator; provides Mg and buffering capacity \\[2pt]
L-Carnitine (as L-carnitine tartrate)               & 7.5000000 & Supports fat metabolism; useful with added fish oil \\[2pt]
Glucosamine HCl                                     & 6.000000  & Joint-support amino-sugar; heat-stable through retort \\[2pt]
Betaine (Trimethylglycine)                          & 6.000000  & Hepatic methyl donor and osmolyte; supports liver function \\[2pt]
Potassium citrate (tripotassium citrate)            & 5.000000  & Urinary pH control and citrate chelation \\[2pt]
Collagen peptides (hydrolysed bovine)               & 5.000000  & Provides glycine/proline for connective tissue; improves mouthfeel \\[2pt]
Methylsulfonylmethane (MSM)                         & 4.000000  & Sulfur donor; complements glucosamine for joint health \\[2pt]
Zinc bisglycinate chelate (25\% Zn)                 & 3.000000  & Chelated zinc to meet AAFCO requirements \\[2pt]
Iron proteinate (20\% Fe)                           & 2.000000  & Chelated iron to meet AAFCO Fe targets \\[2pt]
DL-Methionine (USP grade)                           & 3.500000  & Sulfur amino acid and urinary acidifier support \\[2pt]
Vitamin K$_2$ (Menaquinone--7, 1\% assay)           & 1.700000  & ≈17\,\textmu g MK-7 per pouch; aids Ca utilisation \\[2pt]
L--Cysteine (USP grade)                             & 0.500000  & Complements methionine for sulfur balance \\[2pt]
Selenium yeast (0.20\% Se)                          & 0.550000  & Delivers ≈11\,\textmu g Se per pouch \\[2pt]
Copper proteinate (10\% Cu)                         & 0.300000  & Trace mineral meets AAFCO limits \\[2pt]
Niacin (B$_3$)                                      & 0.250000  & Metabolic cofactor \\[2pt]
Thiamine (B$_1$)                                    & 0.190000  & Heat-labile B vitamin; overage included \\[2pt]
Manganese proteinate (10\% Mn)                      & 0.150000  & Trace mineral floor \\[2pt]
Vitamin D$_3$ (cholecalciferol, 100{,}000 IU g$^{-1}$) & 0.115000 & Provides ≈115 IU per pouch \\[2pt]
Vitamin E (DL--α--tocopheryl acetate, 400 IU g$^{-1}$)& 0.065000 & Antioxidant; retort overage included \\[2pt]
Riboflavin (B$_2$)                                  & 0.050000  & Energy cofactor \\[2pt]
Pyridoxine (B$_6$)                                  & 0.050000  & Amino-acid metabolism cofactor \\[2pt]
Vitamin A (retinyl palmitate, 320{,}000 IU g$^{-1}$)& 0.040000  & Provides ≈100 IU per pouch; overage for retort loss \\[2pt]
Potassium iodate (KIO$_3$)                          & 0.015000  & ≈90\,\textmu g I per pouch \\[2pt]
Biotin (Vitamin B7), Pharma-grade D-Biotin          & 0.008000  & Skin/coat support (≈80\,\textmu g per pouch) \\[2pt]
\midrule
Mixed tocopherols (($\alpha:\beta:\gamma:\delta$) =1.0:0.3:6.0:2.0 50\% active powder) & 1.000000  & Antioxidant for shelf-life stability support, not full dietary E \\[2pt]
\midrule
Anti-caking carrier (q.s.)                         & 1.000000  & Flow aid; adjusted to bring total premix to 100.000000 g \\[2pt]
\midrule
\textbf{Total}                                     & \textbf{100.000000 $\pm$0.1} & One 100 g DogPro premix packet per 10 kg run. MOQ 10 Packets. \\
\bottomrule
\end{longtable}

% ------------------- NOTES -------------------
\vspace{1em}
\subsection*{Composition for DogCorePro}
\begin{table}[h]
\centering
\caption{DogCorePro Composition per 10 kg run (or 100 pouches)}
\label{tab:dogcore_composition_}
\begin{tabular}{@{}l r r@{}}
\toprule
\textbf{Component} & \textbf{Dose per 10 kg} & \textbf{Per pouch} \\
\midrule
DogCore Premix & 6500g & 65g \\ [3pt]
Omega-3 Fish Oil PV<=5.0meq/Kg & 250ml & 2.50ml \\[3pt]
DogPro Premix & 100 g & 1.0 g \\[3pt]
Mixed tocopherol liquid Premix & 100 ml & 1.0 ml \\[3pt]
Palatant Liquid Premix & 100ml & 1.0ml \\[3pt]
\midrule
Rendered Bone Broth & 4200g & 42.0g \\[3pt]
\midrule
Nett Weight per pouch & 112.5g pre-retort & 101.5g $\pm$0.50; declared weight 100.00g\\[3pt]
\bottomrule
\bottomrule
\end{tabular}
\end{table}
% ------------------- NOTES -------------------
\vspace{1em}

\subsection*{Composition for DogCorePro}
\noindent\textbf{Composition Notes:}
\begin{itemize}
\item\textbf {DogCore Premix: } Provides high quality protien powders and Calcium to be paired 1:1 with CatCorePro meat pouches.
\item \textbf{DogCore Premix Useage: }6.5 Kg per 10 kg production run of DogCore or 65.0 g per 100 g wet food pouch.
\item \textbf{DogPro Premix: } Complements DogCore Protein-Ca Premix with complete essential vitamins, minerals and chelators and adequate retort loss overage. 
\item\textbf{AAFCO Compliance: } Together DogCore and DogPro meets AAFCO requirements for complete and balanced nutrition when paired with CatCore and CatPro as per diet chart. 
\item\textbf{Design Overages: }Enhanced taurine formulation for cardiac health support. Vitamin A is balanced carefully with daily 4.0g fresh liver from 2 CatCore pouches to avoid stacking. Ca:P >=1.4:1 within AAFCO recommended limits when paired with CatCorePro pouches as per diet chart. 
\item \textbf{Antioxidant Premix: } Provides Primary Vitamin E (dl-$\alpha$tocopheryl) and mixed antioxidants for enhanced oxidative stability.
\item \textbf{Omega-3 Fish Oil Blend:} Provides omega 3:omega 6  balance
\item \textbf{Palatant Premix: } Meat Hydrolyasants for enhanced palatability.
\item\item{Rendered Goat Bone Broth: } Solvent base for retort processing; improves hydration, adds collagen, chondoitin and other bone joint stability nutrients. 
\item \textbf{NO Alginate Gel - Ca Premix:} No alginate gel in this SKU. Forms slurry consistancy. 
\item \textbf{Low Sodium:} DogCore provides $\approx$ 14.0 mg Na per 100g wet food. Palatant Premix provides additional 47.0mg Na to meet electrolyte balance requirements ($\approx$ 0.061\% Na w/w) as per AAFCO when paired with CatCorePro pouches as per diet chart. 
\end{itemize}