% dog_feeding_lanes.tex
% Comprehensive dog feeding guidelines

\begin{flushleft}
\textbf{Growlrr Dog Feeding Lanes — Canonical Advisory}\\[4pt]
Each pouch (100\,g) supplies about 120\,kcal. 
Curd + rice mix (150\,g rice + 100\,g curd $\approx$ 300\,kcal) forms the fresh staple. 
Feeding pattern scales by body weight and activity.
\end{flushleft}

\vspace{3mm}

\begin{longtable}{@{} c p{2.5cm} c c c p{7.5cm} @{}}
\caption{Growlrr Dog Feeding Lanes by Breed Size}\\
\toprule
\textbf{Lane} & \textbf{Breeds} & \textbf{Wt} & \textbf{kcal} & \textbf{Meals} & \textbf{Feeding Advisory}\\
 & & \textbf{(kg)} & \textbf{/day} & & \\
\midrule
\endfirsthead

\multicolumn{6}{c}{\tablename\ \thetable\ -- continued}\\
\toprule
\textbf{Lane} & \textbf{Breeds} & \textbf{Wt} & \textbf{kcal} & \textbf{Meals} & \textbf{Feeding Advisory}\\
 & & \textbf{(kg)} & \textbf{/day} & & \\
\midrule
\endhead

\midrule
\multicolumn{6}{r}{\textit{Continued on next page}}\\
\endfoot

\bottomrule
\endlastfoot

1 — Toy/Mini & Chihuahua, Pomeranian, Toy Poodle & 2–5 & 250–350 & 2 & ½ CatCore + ½ DogCore + 150 g curd-rice + 20 g veg per meal\\[6pt]

2 — Small & Beagle, Cocker Spaniel, Fr. Bulldog & 6–10 & 400–550 & 2 & 1 CatCore + 1 DogCore + 250 g curd-rice + 20 g veg per meal\\[6pt]

3 — Medium & Indie, Border Collie, Shiba Inu & 11–20 & 600–900 & 2 & 1 CatCore + 1 DogCore + 250–300 g curd-rice + 20 g veg per meal\\[6pt]

4 — Large & Labrador, Golden, Boxer & 21–35 & 1000–1500 & 3 & 1 CatCore + 1 DogCore + 250 g curd-rice + 20 g veg per meal\\[6pt]

5 — X-Large & Rottweiler, GSD, Husky & 36–50 & 1600–2000 & 3 & 1 CatCore + 1 DogCore + 300 g curd-rice + 20 g veg per meal\\[6pt]

6 — Giant & Great Dane, Mastiff, St Bernard & 50+ & 2200–2800 & 3 & 1 CatCore + 1 DogCore + 350 g curd-rice + 20 g veg per meal\\[6pt]

\end{longtable}

\vspace{4mm}

\begin{flushleft}
\textbf{Feeding Rules}\\[2pt]
CatCore + DogCore pairing supplies the full amino acid and micronutrient spectrum. 
Curd-rice delivers digestible carbohydrate, calcium, and probiotics; use 4\%-fat whole-milk curd and plain cooked rice in 3:2 ratio. 
Include 20–30 g/day boiled vegetables. 
Feed twice daily for dogs $\leq$ 20 kg and thrice daily for dogs $>$ 20 kg. 
Ensure constant access to clean water; broth and curd contribute to hydration.
Consult our Vet on growlrr.com for any prior lactose/dairy allergy.
\end{flushleft}

\vspace{6mm}

\begin{flushleft}
\textbf{Approved Vegetable Add-ins for Dogs}\\[4pt]
All vegetables are boiled or lightly steamed, unseasoned, and unsalted.
\end{flushleft}

\vspace{3mm}

\begin{tabularx}{\linewidth}{@{} l l l X @{}}
\toprule
\textbf{Vegetable} & \textbf{Portion (g)} & \textbf{Home Measure} & \textbf{Notes}\\
\midrule
Carrot & 20 & ¼ medium carrot, cubed & Beta-carotene\\[3pt]
Green peas & 20 & 2 tbsp, mashed & Mild protein + fiber\\[3pt]
Zucchini & 20 & ¼ cup slices & Low-oxalate filler\\[3pt]
Spinach / Kale purée & 20 & 1 heaped tbsp & Iron + antioxidants ---Max once per week\\[3pt]
Green beans & 20 & 3–4 beans, mashed & Safe fiber\\[3pt]
Sweet potato & 20 & 1 tbsp mash & Slow carbs\\[3pt]
Pumpkin & 20 & 2 tbsp mash & Gut motility\\[3pt]
Banana (fruit) & 15 & 2–3 slices & Occasional dessert/treat --- Max once per week\\[3pt]
\bottomrule
\end{tabularx}

\vspace{4mm}

\begin{flushleft}
\textbf{Feeding Notes}\\[2pt]
Avoid onions, garlic, broccoli, cauliflower, or starchy fillers. 
Keep total vegetable content near 10-20g/meal or as noted. 
\end{flushleft}

\vspace{6mm}

\begin{flushleft}
\textbf{Approved Dairy Options for Dogs}\\[4pt]
Use whole-milk  fresh culture curd/yogurt (4\% fat minimum) for optimal calcium and probiotic benefit. 
Plain, unsweetened varieties only.
Curd/Yogurt should be fresh and refridgerated. Discard if discolored, water seperates or smells rancid. 
Always introduce dairy gradually. Watch for signs of lactose intolerance. Consult our vet at www.growlrr.com if needed

\end{flushleft}

\vspace{3mm}

\begin{tabular}{@{} l l l p{7cm} @{}}
\toprule
\textbf{Dairy Type} & \textbf{Portion (g)} & \textbf{Home Measure} & \textbf{Notes}\\
\midrule
Fresh Plain whole-milk curd & 100 & ½ cup & Calcium, probiotics\\[3pt]
Fresh Plain Greek yogurt with live probiotic culture & 100 & ½ cup & Higher protein\\[3pt]
Paneer (cottage cheese) & 30 & 2 tbsp crumbled & High protein + calcium --- only as backup\\[3pt]
Buttermilk (chaas) & 50 & ¼ cup & Hydration + probiotics --- only as backup\\[3pt]
\bottomrule
\end{tabular}

\vspace{4mm}

\begin{flushleft}
\textbf{Dairy Notes}\\[2pt]



\end{flushleft}



