% Suggested filename: chapters/02_preface.tex

This binder describes the Growlrr pilot formulations, standard operating procedures for building the product, bill of materials,incomming and outgoing QC, regulatory framework, nutritonal audits for formulation and appendices. Values are design assumptions for pilot runs and are intended to be validated by finished-product assays. Standards and raw-ingredient data are cited in the bibliography. All SKUs meet baseline nutrient standards for labeling.

The present pilot study has been designed as a \textbf{60 kg retort validation run} with \textbf{6 distinct recipes}
\textbf{10 kg each}, retort stabilised and packed into standardized \textbf{100 g pouches}. We deliberately use \textbf{pouches rather than cans} at this stage, since pouch retort facilities are cost-accessible, and they provide sufficient resolution to measure our primary objectives. The learnings from pouches are fully translatable to cans for subsequent scale-up.

\subsection*{Objectives of the Pilot Run}
\begin{enumerate}[leftmargin=1.5em]
  \item \textbf{Nutrient assays:} Verify macro- and micro-nutrient retention post-retort against AAFCO/FEDIAF floors and ceilings.
  \item \textbf{Shelf-life testing:} Establish accelerated shelf life values with rancidity, oxidation, and microbial profiles.
  \item \textbf{Structural integrity:} Assess gel matrix stability, phase separation, and form factor.
  \item \textbf{Palatability:} Track voluntary intake, preference, and tolerance in animals across SKUs.
  \item \textbf{Ingredient validation:} Confirm that each SKU's ingredient design performs as expected under thermal processing.
  \item \textbf{Process validation:} Confirm reproducibility of SOP steps (solid prep, blanch, liquid assembly, premix dosing, sealing, retort profile).
  \item \textbf{Sub-optimisation testing:} Fine-tune gel matrix, chelators, palatants, tocopherol distribution, and retort curve.
  \item \textbf{Credibility:} Generate assay-backed evidence that Growlrr's rotation logic, premix dosing, and paired-SKU genome strategy are regulator-ready and consumer-safe.
\end{enumerate}

This pilot is therefore not only a technical validation but also a credibility-building exercise. It demonstrates the safety, stability, and innovation of Growlrr's formulations under real-world processing conditions, bridging design assumptions to empirical data.