% Suggested filename:05a_introduction_catcore_parta.tex
% Part A: Main text
\section*{Introduction to CatCore}

Welcome to the Growlrr universe: a unique, modular, rotational feeding system built on species-appropriate, whole natural ingredients. Each recipe is organ-forward, balanced with muscle and supportive tissues, and carefully fortified to safely meet AAFCO/FEDIAF compliance. There are no grains, no fillers, no gimmicks --- only biologically aligned formulations rooted in whole-prey logic, adapted for everyday feeding convenience across all life stages.

\subsection*{The Six CatCore SKUs}

Growlrr's feline system is expressed in six locked SKUs, each a distinct organ-forward recipe. They are paired into bonded ``base pairs'' using a light--dark color code system, ensuring owners always feed one light + one dark pouch per day. This makes compliance foolproof at the consumer level.

To make this simple for owners, every SKU is \textbf{color-coded and named} by its anchor ingredient:

\begin{itemize}[leftmargin=1.5em]
\item \textcolor{lightblue}{$\blacksquare$} Chicken Heart (Light Blue)
\item \textcolor{darkblue}{$\blacksquare$}  Sardine (Dark Blue)
\item \textcolor{lightblue}{$\blacksquare$} Chicken Liver (Light Red)
\item \textcolor{darkbrown}{$\blacksquare$} Chicken Gizzard (Dark Red)
\item \textcolor{lightbrown}{$\blacksquare$} Goat Kidney (Light Brown)
\item \textcolor{darkbrown}{$\blacksquare$}  Goat Spleen (Dark Brown)
\end{itemize}

The Growlrr app translates this into daily diet charts --- easy to follow at a glance, backed by clinical rigor.

\subsection*{Example: Meet Bella the Cat (4.0 kg, indoor, adult)}

Bella thrives on rotation. Her \textbf{weekly chart} is shown in Table~\ref{tab:bella_rotation}.

Each pouch delivers full compliance; the rotation ensures diversity of proteins, amino acids, and micronutrients, with no monotony.

Each pair balances nutrients in a complementary way: heart and sardine pair balance taurine and phosphorus loads over the day; liver and gizzard pair smoothens out vitamin A  and taurine peaks;  kidney and spleen are both non-poultry hypoallergenic pairs with mineral rich high quality protines. Individual SKU is designed to meet Ca:P ratio of 1.1 or greater. This ``nutritional genome'' framework encodes safety into packaging, without owners needing spreadsheets or nutritional degrees.

\subsection*{Why Rotation?}

Why do we design this way, instead of offering one fixed ``complete'' SKU or a rack of multiple, non-interlocking flavors as most brands do? Because animals do not thrive on monotony, nor on randomized variety. Rotation allows for\cite{ref3,ref12,web6,web75}:

\begin{itemize}[leftmargin=1.5em]
  \item Natural smoothing of nutrient peaks and valleys across days.
  \item Exposure to different organ and muscle profiles, reducing allergen risk\cite{web27,web32,web76,web77,web83} and avoiding chronic overload of any single nutrient.
  \item Built-in behavioral enrichment --- meals taste different, but within a consistent logic that keeps nutrition safe.
  \item A regulator-ready compliance story: daily safety, weekly completeness, minimal SKU proliferation.
\end{itemize}

Growlrr's system is not ``flavors.'' It is a structured code, a genome of nutrition, where pairs interlock like base-pairs in DNA. The result: biological precision with consumer simplicity. Pet owners can generate their free customized diet chart\cite{ref10} from our website (\url{www.growlrr.com/diet/}), schedule online chat or call with a pet nutritionist or vet, interact with our trained AI to learn more about each ingredient in our pouch, source, traceability and quality.
