\subsection*{Appendix B8 --- Copper and Manganese Strategy\cite{ref6}}

\textbf{Background:}  
Copper (Cu) and manganese (Mn) are trace minerals with critical enzymatic roles:  
- Copper: cofactor in hemoglobin synthesis, connective tissue enzymes, pigmentation.  
- Manganese: cofactor in cartilage/bone metabolism, antioxidant enzymes.  
Both are required in very small amounts, and chronic excess causes accumulation (liver Cu storage disease in cats/dogs).

\textbf{Regulatory Standards (AAFCO/FEDIAF, per 1000 kcal):}  
\begin{itemize}[leftmargin=1.2em]
  \item Copper: floor 1.0 mg; ceiling 250 mg  
  \item Manganese: floor 1.25 mg; ceiling 36 mg  
\end{itemize}

\textbf{Locked Premix Baseline (per pouch, via CatPro/DogPro @1 g/pouch):}  
\begin{itemize}[leftmargin=1.2em]
  \item Copper: 0.015 g / 100 g premix $\rightarrow$ ~1.5 mg/pouch $\rightarrow$ ~1.2 mg/1000 kcal  
  \item Manganese: 0.030 g / 100 g premix $\rightarrow$ ~3.0 mg/pouch $\rightarrow$ ~2.4 mg/1000 kcal  
\end{itemize}

\textbf{Natural Ingredient Contribution (per pouch, literature values):}  
\begin{itemize}[leftmargin=1.2em]
  \item Copper: liver (0.2--0.4 mg/g), kidney (0.05--0.1 mg/g), yolk (trace). With 2--5 g liver, adds ~0.5--1.0 mg/pouch.  
  \item Manganese: pumpkin (0.15--0.2 mg/100 g), egg yolk (trace), meat negligible. Adds ~0.02--0.05 mg/pouch.  
\end{itemize}

\textbf{Post-Retort Loss Assumptions:}  
- Copper and manganese are heat stable.  
- No overage needed; premix delivers controlled levels.

\textbf{Compliance Statement:}  
- Copper: ~1.2 mg/1000 kcal (premix) + ~0.5 mg food = ~1.7 mg/1000 kcal. Safely above 1.0 mg floor, <1\% of 250 mg ceiling.  
- Manganese: ~2.4 mg/1000 kcal (premix) + ~0.05 mg food = ~2.5 mg/1000 kcal. Safely above 1.25 mg floor, <10\% of 36 mg ceiling.

\textbf{SOP Notes:}  
\begin{enumerate}[leftmargin=1.2em]
  \item Premix is the main Cu and Mn source; organs contribute modest Cu only.  
  \item Keep liver $\leq$5 g/sku to avoid Cu accumulation.  
  \item No extra Mn fortification --- pumpkin/yolk are sufficient buffers.  
  \item Annual batch assays to verify Cu accumulation is avoided in long-term feeding lanes.  
\end{enumerate}

\textbf{Outcome:}  
- Copper = green (conservative, buffered).  
- Manganese = green (well above floor, far below ceiling).  
- Together: balanced against Zn and Fe in Appendix A7 to maintain safe trace mineral profile.
