\subsection*{Bill of Materials: CatCore Gizzard SKU}
\label{bom:catcore_heart}

\subsubsection*{Batch Specifications}
\begin{itemize}
\item Batch size: 10 kg (100 pouches)
\item Per pouch declared weight: 100 g
\end{itemize}

\subsubsection*{Raw Ingredients}
\begin{table}[h]
\centering
\caption{CatCore Gizzard (Chicken) SKU - Raw Materials per 10 kg Batch}
\begin{tabular}{@{}llrrrp{4cm}@{}}
\toprule
\textbf{Ingredient} & \textbf{Per Batch (Kg)} & \textbf{Prep Method}  & \textbf{Traceability Log} & \textbf{Prep Notes} & \textbf{Obs}\\
\midrule
Chicken gizzard     & 2.400 $\pm$0.08  & Diced 1.5cm            & [QC-FORM-\_\_\_\_\_\_] & Remove grit, uniform cubes & Refrigerate\\
Chicken frame mince & 2.000 $\pm$0.05  & Fine grind 5mm sieve   & [QC-FORM-\_\_\_\_\_\_] & Follow Bone Broth SOP 30-B. No grit or sharp particles & Refridgerate  \\
Chicken muscle cuts & 1.100 $\pm$0.08  & Diced 1.5cm            & [QC-FORM-\_\_\_\_\_\_] & Trim fat, uniform cubes & Refrigerate\\
Chicken heart       & 1.000 $\pm$0.05  & Diced 1.5cm            & [QC-FORM-\_\_\_\_\_\_] & Trim vessels, uniform cubes & Refrigerate\\T TOLERANCE \\ 
\midrule
\textbf{TOTAL SOLIDS} & \textbf{6.500 $\pm$0.05} & Caliburated Scale & [QC-FORM-\_\_\_\_\_\_] & Refridgerate and maintain Cold Chain Logs & MAINTAIN TIGHT TOLERANCE \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection*{Processing Instructions}
\item Thoroughly wash all meat products in running hot jet stream water for 5 minutes to wash off any blood, coagulants, debris and other undesirable particles. 
\textbf{Solid Preparation (1.5cm Standard):}
\begin{itemize}
\item Measure out each raw ingredient using caliburated scale and tight tolerance. Keep the rest refrigerated. 
\item Use sharp knife or dicer machine
\item All diced ingredients: uniform 1.5cm$\pm$ 0.5cm cubes
\item Maintain strict cold chain logs before, during and after prep (4 deg C)
\item Measure each ingredient post dicing and note down the weight. 
\item Refridgerate immediately before proceeding to next ingredient. 
\item Keep preperation time to under 20 minutes to control pathogen load. 

\end{itemize}
\textbf{Frame Mince:}
\begin{itemize}
\item Chicken Bone Mince as per Bone Broth-SOP 30-B
\item Pass through 5mm sieve twice as per Bone Broth 
\item Should be fine paste with no large bone fragments. Reject if shards present. Maintain coldchain Logs
\end{itemize}

\subsubsection*{Liquid Components}
\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Component} & \textbf{Per Batch (kg)  & \textbf{Per Pouch (g)}} \\
\midrule 
Chicken Bone broth (Follow SOP 30-B) &  4.10 $\pm$0.10 & 41.0 \\
Blanch water (process recovery-refer SOP 30-A) & 0.250$\pm$0.010 & 2.5 \\
\textbf{TOTAL LIQUIDS} & \textbf {4.350} & {43.5} \textbf \\
\midrule

\bottomrule

\end{tabular}

\vspace{1em}

\begin{itemize}
\item \textbf{CatPro Premix: } Complements CatCore Fresh Proteins with complete essential vitamins, minerals and chelators and adequate retort loss overage.
\item \textbf{Useage:} 100 g per 10 kg production run or 1.0 g per 100 g wet food pouch complements with complete essential vitamins, minerals and chelators. \item\textbf{AAFCO Compliance: } Meets AAFCO requirements for complete and balanced nutrition.
\item\textbf{Design Overages: }Enhanced taurine formulation for cardiac health support. Vitamin A is balanced carefully with daily 4.0g fresh liver from 2 CatCore pouches to avoid stacking.\cite{ref64}.  
\item \textbf{Omega-3 Fish Oil Blend:}250ml Omega-3 Fatty Acid Fish Oil PV<=5.0meq/Kg is added per 10Kg run or 2.5ml per per 100g wet food pouch except sardine SKU.
\item \textbf{Antioxidant Premix: } 100ml per 10Kg run or 1ml per 100g wet food pouch. Provides Primary Vitamin E (dl-$\alpha$tocopheryl) and blended organic antioxidants for enhanced oxidative stability.
\item \textbf{Alginate Gel - Ca Premix:} 100g per 10Kg run.  Forms gel under retort heat. Delivers additional 80mg dietary Ca per 100g wet food pouch.
\item \textbf{Palatant Premix: } 100ml per 10Kg run or 1ml per 100g wet food pouch.
\end{itemize}
