
\section*{Incoming Premix QC \& Dispensing SOP}
\addcontentsline{toc}{section}{Incoming Premix QC \& Dispensing SOP}
\textbf{Scope:} Covers all Growlrr premixes

\begin{table}[h]
\centering
\begin{tabular}{lll}
\hline
\textbf{Premix Type} & \textbf{Packaging} & \textbf{MOQ} \\
\hline
\multicolumn{3}{l}{\textbf{Solid Premix:}} \\
CatPro V5 Premix & 100g sealed pouches & 1.5Kg \\
DogCore V5 Premix & 100g sealed pouches & 1.5Kg \\
DogPro V5 Premix & 100g sealed pouches & 1.5Kg \\
Alginate Gel - Encapsulated Calcium Premi & 100g sealed pouches & 1.5Kg \\
\hline
\multicolumn{3}{l}{\textbf{Liquid Premix:}} \\
Palatant V5 Premix & 100ml sealed amber bottles & 1.5L \\
Blended Antioxidant V5 Premix & 100ml sealed amber bottles & 1.5L \\
Shelf Stable Blended Omega-3 Fish Oil & 250ml sealed amber bottles & 1.5L \\
\hline
\end{tabular}
\end{table}

\subsection*{1. Receipt \& Identification}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item Verify seals and labels on arrival.
  \item Cross-check supplier COA with Growlrr specification \& file it in Build Binder.
  \item Assign internal Lot ID: \texttt{PREMIX-TYPE/YYYYMMDD/SEQ}.
  \item Create Forms QC-Premix-01, QC-Premix-02, QC-Premix-03 for Incoming Materials log, Test method and Acceptance log, Non-compliance/Damage or Reject log.
  \item Record incoming premix packs in Form QC-Premix-01; store verified packets $\leq$25$^\circ$C, RH $<$ 60\%.
  \item Rejected lots should be recorded in Form QC-Premix-03 with supervisor sign-off and samples preserved for inspection. 
\end{enumerate}

\subsection*{2. Subdivision \& Labeling}
\begin{enumerate}[leftmargin=*,noitemsep]
  \item Portion solids into 100 g and liquids into 100 mL packs.
  \item Label each pack with name, Lot ID, date, net quantity, operator initials.
  \item Mark ---"For Internal Use Only --- add entire pack per 10 kg run.---"
  \item Retain one sealed control pack per lot for 24 months.
\end{enumerate}

\subsection*{3. Verification Tests}
\begin{tabularx}{\linewidth}{@{}l l X@{}}
\toprule
Test & Method & Acceptance \\
\midrule
Weight & Electronic balance & $\pm$ 0.5 g from target \\
Moisture (solid) & Moisture meter & Within spec \\
Visual & Free-flowing, no lumps & Pass \\
Label & Correct name, lot, date & Pass \\
Incoming COA & Supplier COA with traceability on file & Pass \\
\bottomrule
\end{tabularx}
\item Record log in Form QC-Premix-02 and save  copy for Floor use sign-off during production \\

\subsection*{4. Storage}
Solids: $\leq$ 25$^\circ$C, dry; Liquids: amber HDPE, avoid sunlight. FIFO by Lot ID. Maintain all entry/ exit logs. 

\subsection*{6. Documentation}
Maintain:
\begin{itemize}[noitemsep]
  \item Binder with all Supplier documents, COA, receipts, Forms QC-Premix-01, QC-Premix-02 and QC-Premix-03
  \item Scan and digitize the binder at the time of completion of production and upload to cloud server. 
\end{itemize}


