% LaTeX fragment — Omega-3 Fish Oil Specification (Shelf-Stable, Low-Oxidation)

\textit{Omega-3 Fish Oil — Pre-stabilised, Shelf-Stable (Low PV / Low Hg)}

\begin{itemize}
  \item \textbf{Product type:} Refined and deodorised marine triglyceride oil (fish origin, e.g. sardine / anchovy / menhaden).

  \item \textbf{Function:} Energy enrichment and EPA/DHA source for feline wet diets; provides omega-3 balance and improved skin–coat nutrition.

  \item \textbf{Dosage:} 250\,mL per 10\,kg production run (≈2.5\,mL per 100\,g pouch, ≈2.3\,g oil/pouch).

  \item \textbf{Packaging:} 250\,mL amber HDPE bottles; minimum order 1.5 L (6 × 250 mL). Nitrogen-flushed and induction-sealed.

  \item \textbf{Composition:}
    \begin{itemize}
      \item Total omega-3 (EPA + DHA) ≥ 30 \% of fatty acids (≥ 300 mg/g oil).
      \item Triglyceride form ≥ 90 \%.
      \item Antioxidant system: mixed tocopherols 0.05 – 0.10 \%; optional rosemary extract ≤ 0.02 \%.
      \item No synthetic flavour, colour, or added stabilisers beyond tocopherols/rosemary.
    \end{itemize}

  \item \textbf{Quality parameters:}
    \begin{itemize}
      \item Peroxide value (PV) ≤ 2 meq O₂ kg⁻¹.
      \item p-Anisidine value (AV) ≤ 10.
      \item Totox (2 × PV + AV) ≤ 14.
      \item Moisture ≤ 0.05 \%.
      \item Acid value ≤ 1 mg KOH g⁻¹.
      \item Heavy metals: mercury < 0.05 ppm, lead < 0.1 ppm, arsenic < 0.1 ppm, cadmium < 0.05 ppm.
      \item PCB + dioxin < 0.09 pg TEQ g⁻¹.
    \end{itemize}

  \item \textbf{Physical:} Clear, light-gold liquid; density 0.92 ± 0.02 g mL⁻¹ at 25 °C; no precipitate or clouding ≥ 10 °C.

  \item \textbf{Shelf life:} 12 months sealed at ≤ 25 °C; 18 months refrigerated (4 °C). Protect from light and air.

  \item \textbf{Microbiology:} Not applicable (oil matrix, sterile by refining).

  \item \textbf{Thermal compatibility:} Stable at 45 °C for 30 min; withstands retort in emulsion form without visible phase separation.

  \item \textbf{Sensory:} Neutral odour and taste; no rancid or fishy off-note; colour Lovibond ≤ 5Y, ≤ 0.5R.

  \item \textbf{Label declaration:} “Fish oil (pre-stabilised with natural tocopherols and rosemary).”

  \item \textbf{Supplier CoA must report:}
        PV, AV, Totox, EPA \%, DHA \%, acid value, moisture, heavy-metal panel, antioxidant \%, and bottling date.
\end{itemize}
