% LaTeX fragment — Palatant Specification (shelf-stable version)
\textit{Palatant — Meat Hydrolysate Liquid (Thermostable, Shelf-Stable)}

\begin{itemize}
  \item \textbf{Product type:} Enzymatically hydrolysed poultry or marine protein concentrate, liquid form.
  \item \textbf{Function:} Palatability enhancer and omega-3 odour mask for wet feline diets.
  \item \textbf{Dosage:} 100\,mL per 10\,kg production run (≈1\,mL per 100\,g pouch).
  \item \textbf{Physical form:} Homogeneous brown liquid; viscosity 1–3 Pa·s at 25 °C; density 1.05 ± 0.05 g mL⁻¹.
  \item \textbf{Composition:}
    \begin{itemize}
      \item Hydrolysed animal protein ≥ 45 \% (dry basis).
      \item Peptides < 3 kDa ≥ 60 \% of protein fraction.
      \item Sodium ≤ 2 \%.
      \item Moisture 45–55 \%.
      \item Shelf-stable antioxidant system: Rosemary extract 0.10 \%.
      \item Preservative: potassium sorbate 0.10 \%.
      \item Emulsifier:Glycerol monostearate GMS 0.1\%
      \item pH 5.5 – 6.5 (as supplied).
    \end{itemize}
  \item \textbf{Thermal stability:} Withstands retort (121 °C × 30 min) without phase separation or burnt odour.
  \item \textbf{Shelf life:} 12 months at ≤ 25 °C; 18 months refrigerated (4 °C); store sealed, away from light and air.
  \item \textbf{Microbiological limits:}
    \begin{itemize}
      \item Total plate count < 10³ cfu g⁻¹.
      \item Yeast \& mould < 10² cfu g⁻¹.
      \item Pathogens absent.
    \end{itemize}
  \item \textbf{Additives not permitted:} no synthetic flavour, colour, or MSG.
  \item \textbf{Sensory:} Rich meaty aroma; no rancid or sulphidic notes.
  \item \textbf{Label declaration:} “Natural meat(non-poultry) hydrolysate (palatant).”
  \item \textbf{Supplier CoA must include:} protein \%, Na \%, preservative \%, moisture \%, pH, microbiology, retort-stability report.
\end{itemize}
