%------------------------------------------------------------
% Incoming Raw Material QC & Storage SOP (Rev H-3.0.0)
%------------------------------------------------------------

\clearpage
\section*{Incoming Raw Material QC \& Storage SOP}

\subsection*{1. Scope}
Applies to all animal-derived and perishable inputs for Growlrr CatCore and DogCore lines: hearts, gizzards, livers, kidneys, spleens, frame mince, muscle meats, sardine, fish bone meal, egg yolk powder, chicken and goat frames, trotters, neck, back frame and bones for broth, red pumpkin and ancillary dry materials.

\subsection*{2. Receiving Procedure}
\begin{itemize}\setlength\itemsep{2pt}
  \item Check \textbf{delivery temperature} on arrival. Frozen: $\leq$ -18\textdegree C; Chilled: 0-4\textdegree C; Dried powders: ambient $\leq$ 25\textdegree C, RH $\leq$ 65\%.
  \item Inspect \textbf{packaging}: intact, labelled with supplier, lot \#, weight, COA reference.
  \item Record receipt: time, supplier, lot \#, temperature, and QC initials.
\end{itemize}

\subsection*{3. Organ \& Meat Blocks (heart, gizzard, liver, lamb, kidney, spleen, lean muscle cuts)}
\begin{tabularx}{\linewidth}{@{}l X X@{}}
\toprule
\textbf{Parameter} & \textbf{Accept} & \textbf{Reject / Action} \\
\midrule
Temp on arrival & $\leq$ 4\textdegree C (chilled) or $\leq$ -18\textdegree C (frozen) & $>$ 5\textdegree C or thawed edges \\
Appearance & Bright natural colour & Grey/green discolouration, sticky film \\
Odour & Clean, fresh & Sour, rancid, putrid \\
Texture & Firm, resilient & Mushy, slimy \\
Foreign matter & None & Visible contamination \\
COA (micro) & TVC $\leq$ 10$^5$ CFU/g; \emph{E. coli} $<$ 10 CFU/g; \emph{Salmonella} Absent/25 g & Fail = Reject \\
\bottomrule
\end{tabularx}

\textbf{Storage:} Chilled lots 0-2\textdegree C (use within 48 h). Frozen lots -18\textdegree C (use within 3 months). Thaw under refrigeration only.

\subsection*{4. Fish (sardine)}
\begin{tabularx}{\linewidth}{@{}l X X@{}}
\toprule
\textbf{Parameter} & \textbf{Accept} & \textbf{Reject / Action} \\
\midrule
Temp & $\leq$ -18\textdegree C (frozen) & $>$ -12\textdegree C \\
Appearance & Bright eyes, metallic skin, firm flesh & Dull eyes, brown gills, soft texture \\
Odour & Clean sea smell & Ammoniac, rancid \\
Hg (COA) & $\leq$ 0.05 ppm & $>$ 0.05 ppm Hg $\Rightarrow$ Reject lot \\
Peroxide PV (COA) & $\leq$ 5.0 meq/kg & $>$ 5.0 meq/kg or missing COA and cold-chain logs $\Rightarrow$ Reject lot if older than 1 week \\
\bottomrule
\end{tabularx}

\textbf{Storage:} -18\textdegree C; thaw at $\leq$ 4\textdegree C and drain before use.

\subsection*{5. Egg Yolk Powder}
\begin{tabularx}{\linewidth}{@{}l X X@{}}
\toprule
\textbf{Parameter} & \textbf{Accept} & \textbf{Reject} \\
\midrule
Moisture & $\leq$ 4\% & $>$ 5\% \\
Colour & Deep yellow to orange & Pale / brown \\
Odour & Clean, eggy & Rancid / musty \\
Micro & TPC $\leq$ 10$^3$ CFU/g; \emph{Salmonella} Absent & Fail = Reject \\
\bottomrule
\end{tabularx}

\textbf{Storage:} airtight sealed vacuum packs, $\leq$ 15\textdegree C, RH $\leq$ 60\%, away from light. Shelf life 12 months unopened.

\subsection*{6. Trotter; neck, frame and bones (for mince and broth)}
\begin{tabularx}{\linewidth}{@{}l X X@{}}
\toprule
\textbf{Parameter} & \textbf{Accept} & \textbf{Reject} \\
\midrule
Temp & $\leq$ -18\textdegree C & Thawed / $>$ -12\textdegree C \\
Cleanliness & No feathers, hide, claws, hooves, dirt, tissue residue & Visible contamination \\
Odour & Neutral & Rancid / decomposing \\
Source & Food-grade, antibiotic-free poultry & Unverified source \\
\bottomrule
\end{tabularx}

\textbf{Storage:} frozen -18\textdegree C; feed directly into broth kettle.

\subsection*{7. Dried Additives \& Powders}
Inspect packaging and COA (valid $\leq$ 6 months). Moisture $\leq$ 6\%; caking = Reject. Store at 20-25\textdegree C, RH $\leq$ 60\%, sealed.

\subsection*{8. Temperature \& Storage Map}
\begin{tabularx}{\linewidth}{@{}l l l l@{}}
\toprule
\textbf{Material} & \textbf{Storage} & \textbf{Range} & \textbf{Max Hold Time} \\
\midrule
Frozen meats / fish / bones & Freezer & -18\textdegree C $\pm$ 2\textdegree C & 3 mo \\
Chilled organs & Chiller & 0-2\textdegree C & 48 h \\
Egg yolk powder & Dry store & $\leq$ 15\textdegree C & 12 mo \\
Dry premixes / hydrolysates & Dry store & 15\textdegree C & 12 mo \\
Tocopherol-lecithin liquid & Refrigerated & 4-8\textdegree C & 6 mo \\
Packaging materials & Clean room & $\leq$ 25\textdegree C & 12 mo \\
\bottomrule
\end{tabularx}

\subsection*{9. Actions}
\begin{itemize}\setlength\itemsep{2pt}
  \item \textbf{Accept:} meets all criteria $\Rightarrow$ Label ``QC Approved''.
  \item \textbf{Hold:} minor deviation; quarantine pending investigation.
  \item \textbf{Reject:} fails safety/COA $\Rightarrow$ return or destroy per SOP.
  \item Record all decisions in \textbf{Incoming Material Log (Form QC-Fresh-01)}.
\end{itemize}