% Suggested filename:05b_introduction_dogcore.tex

\section*{From Cats to Dogs --- The DogCore Extension}

Growlrr's system begins with cats --- obligate carnivores, finely tuned to high-protein, organ-forward diets. From this foundation, we extend the same genome logic to dogs, but adapted for their physiology. Dogs are facultative omnivores\cite{ref2}: they can synthesize certain essential nutrients, they tolerate carbohydrates well, and they thrive across a wider range of macronutrient profiles.

\subsection*{The Golden Mean (DogCore + DogPro)}

Instead of proliferating dozens of dog SKUs across breed sizes, Growlrr encodes a single core dog pouch with high quality and highly digestible protiens --- \textbf{DogCore SKU7}, color-coded \colorbox{goldenorange}{\phantom{X}} golden orange, designed as the ``Golden Mean.'' It was engineered to meet the nutritional needs of a Golden Retriever --- the prototypical mid-sized dog --- and then scales seamlessly up or down for other breeds.

\paragraph{Why this design?}
\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Dense protein base:} DogCore combines soy protein isolate, whey protein concentrate, egg yolk powder, egg white powder and functional lecithin. This leverages both animal and plant proteins, aligned to canine physiology.
  \item \textbf{Omnivore flexibility:} Dogs can derive energy safely from carbohydrate staples. Instead of retorting and shipping grain-heavy fillers, we empower owners to add fresh, digestible staples --- cooked rice and probiotic curd/yogurt --- from their own kitchens.
  \item \textbf{Balanced micros:} DogPro premix delivers a robust, conservative baseline of vitamins (A, D, E, B-complex) and trace minerals (Ca, Fe, Zn, Cu, Mn, Se, I), ensuring every lane clears AAFCO/FEDIAF floors without drifting into excess.
\end{itemize}

\subsection*{Why Not Ship Carbohydrates?}

We believe hauling vast quantities of rice or curd through retort packaging, warehousing, and delivery is unnecessary --- every pet-owning household already has access to these staples. By leaving energy carriers to the home, Growlrr minimizes shipping weight, maximizes freshness, and keeps costs fair. Instead, our pouches carry the critical load: proteins and micronutrients, precisely balanced to regulatory standards.

\subsection*{Scaling Across Breeds and Sizes}

With CatCore, every 100 g pouch was standardized to $\approx$100 kcal. DogCore follows the same unit logic. Scaling across breeds becomes a matter of meals/day and rice+curd quantities:


This modularity means a single DogCore SKU, paired with CatCore and scaled via pantry staples, can safely feed a 4 kg cat or a 40 kg bulldog --- without exploding SKU counts or compromising nutrient safety.


\vspace{6mm}


\subsection*{Example: Ringo the Golden Retriever (28 kg, active adult)}

Meet Ringo, a healthy and happy Growlrr who follows his diet chart and enjoys his 3 meals per day  . Ringo follows his breed appropriate \textbf{DogCore lane} (see overleaf), paired with fresh pantry staples available at home. Each meal = 1 Catcore pouch + 1 \colorbox{goldenorange}{\phantom{X}} DogCore pouch + Fresh Curd rice (250g) + 20g boiled vegetable. See Table~\ref{tab:ringo_bowl}.

% Fixed Ringo's Daily Dog Bowl Table
% Replace the existing table in 05b_introduction_dogcore.tex

\begin{table}[h]
\centering
\caption{Ringo's Daily Dog Bowl (per sitting)}
\label{tab:ringo_bowl}
\begin{tabular}{lll}
\toprule
\textbf{Day} & \textbf{AM} & \textbf{PM} \\
\midrule
Mon & \textcolor{lightblue}{\blacksquare} Chicken Heart + \textcolor{goldenorange}{\blacksquare} DogCore + \textcolor{gray}{\blacksquare} Curd Rice 
    & \textcolor{darkblue}{\blacksquare} Sardine + \textcolor{goldenorange}{\blacksquare} DogCore + \textcolor{gray}{\blacksquare} Curd Rice \\
Tue & \textcolor{lightred}{\blacksquare} Chicken Liver + \textcolor{goldenorange}{\blacksquare} DogCore + \textcolor{gray}{\blacksquare} Curd Rice 
    & \textcolor{darkred}{\blacksquare} Chicken Gizzard + \textcolor{goldenorange}{\blacksquare} DogCore + \textcolor{gray}{\blacksquare} Curd Rice \\
Wed & \textcolor{lightbrown}{\blacksquare} Goat Kidney + \textcolor{goldenorange}{\blacksquare} DogCore + \textcolor{gray}{\blacksquare} Curd Rice 
    & \textcolor{darkbrown}{\blacksquare} Goat Spleen + \textcolor{goldenorange}{\blacksquare} DogCore + \textcolor{gray}{\blacksquare} Curd Rice \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5em}
\noindent\small\textit{Color Key:} 
\textcolor{lightblue}{\blacksquare} \textcolor{darkblue}{\blacksquare}
\textcolor{lightred}{\blacksquare} \textcolor{darkred}{\blacksquare}
\textcolor{lightbrown}{\blacksquare} \textcolor{darkbrown}{\blacksquare} CatCore
+ 
\textcolor{goldenorange}{\blacksquare} DogCore
+ 
\textcolor{gray}{\blacksquare} Home staples (curd + rice)

\vspace{2mm}

\begin{flushleft}
\textbf{Feeding Rules}\\[2pt]
Growlrr's modular CatCore + DogCore pairing supplies the full amino acid and micronutrient spectrum. 
Non-poultry days de-sensitises immune system and reduces allergens
Curd rice + veg  delivers easily accessible fresh and digestible carbohydrate, calcium, and probiotics. 
Use fresh or refridgerated 4\%-fat whole-milk curd and plain cooked rice. Avoid lentils, spice, salt or butter.
Feed as per diet chart with daily pairings and weekly rotation. 
Ensure constant access to clean water.
Consult our Vet on growlrr.com for any prior lactose/dairy allergy or other intolerances. 
\end{flushleft}

\begin{flushleft}
\textbf{Growlrr Dog Feeding Lanes — Canonical Advisory}\\[4pt]
Each pouch (100\,g) supplies about 120\,kcal. 
Curd + rice mix (150\,g rice + 100\,g curd $\approx$ 300\,kcal) forms the fresh staple. 
Feeding pattern scales by body weight and activity.
\end{flushleft}


\noindent\textbf{In short:} With 6 CatCore SKUs and 1 DogCore SKU, Growlrr encodes a complete nutritional system, scaling safely across species, breeds, sizes, and life stages --- delivering physiology-first nutrition with pantry-level practicality.


\input{cookbook/introduction/05d_dog_feeding_lanes}
