% dog_feeding_lanes.tex
% Comprehensive dog feeding guidelines
\newpage
\vspace{3mm}

\begin{longtable}{@{} c p{2.5cm} c c c p{7.5cm} @{}}
\caption{Growlrr Dog Feeding Lanes by Breed Size}\\
\toprule
\textbf{Lane} & \textbf{Breeds} & \textbf{Wt} & \textbf{kcal} & \textbf{Meals} & \textbf{Feeding Advisory per meal}\\
 & & \textbf{(kg)} & \textbf{/day} & & \\
\midrule
\endfirsthead

\multicolumn{6}{c}{\tablename\ \thetable\ -- continued}\\
\toprule
\textbf{Lane} & \textbf{Breeds} & \textbf{Wt} & \textbf{kcal} & \textbf{Meals} & \textbf{Feeding Advisory meal}\\
 & & \textbf{(kg)} & \textbf{/day} & & \\
\midrule
\endhead

\midrule
\multicolumn{6}{r}{\textit{Continued on next page}}\\
\endfoot

\bottomrule
\endlastfoot

1 — Toy/Mini & Chihuahua, Pomeranian, Toy Poodle & 2–5 & 250–350 & 2 & ½ CatCore + ½ DogCore + 120 g curd-rice + 10 g veg per meal\\[6pt]

2 — Small & Beagle, Cocker Spaniel, French Bulldog & 6–10 & 400–550 & 2 & 1 CatCore + 1 DogCore + 150 g curd-rice + 15 g veg per meal\\[6pt]

3 — Medium & Indie, Border Collie, Shiba Inu & 11–20 & 600–900 & 2 & 1 CatCore + 1 DogCore + 200 g curd-rice + 20 g veg per meal\\[6pt]

4 — Large & Labrador, Golden, Boxer & 21–35 & 1000–1500 & 3 & 1 CatCore + 1 DogCore + 200 g curd-rice + 20 g veg per meal\\[6pt]

5 — X-Large & Rottweiler, GSD, Husky & 36–50 & 1600–2000 & 3 & 1 CatCore + 1 DogCore + 300 g curd-rice + 25 g veg per meal\\[6pt]

6 — Giant & Great Dane, Mastiff, St Bernard & 50+ & 2200–2800 & 3 & 1 CatCore + 1 DogCore + 350 g curd-rice + 30 g veg per meal\\[6pt]

\end{longtable}

\vspace{1mm}

With easily available kitchen staples like fresh rice,oats, curd, yogurt and vegetables, Growlrr is able to scale from 4.0 Kg cat diet to 40 Kg Rotweiller with just 7 variants and customised diet charts. This is possible because unlike other brands Growlrr does not package and ship carbohydrates and vegetables which are availabe for cheap in every kitchen. Instead we focus on nutrient rich protiens and organs and precise vitamin and mineral balance and a diet chart that is customised for every animal's dietary needs. 
\newpage

\begin{flushleft}
\textbf{Approved Vegetable Add-ins for Dogs}\\[4pt]
\end{flushleft}

\vspace{3mm}

\begin{tabularx}{\linewidth}{@{} l l l X @{}}
\toprule
\textbf{Boiled vegetable option per meal} & \textbf{Portion (g)} & \textbf{Home Measure} & \textbf{Notes}\\
\midrule
Carrot & 20 & ¼ medium carrot, cubed & Beta-carotene\\[3pt]
Green peas & 20 & 2 tbsp, mashed & Mild protein + fiber\\[3pt]
Zucchini & 20 & ¼ cup slices & Low-oxalate filler\\[3pt]
Spinach / Kale purée & 20 & 1 heaped tbsp & Iron + antioxidants ---Max once per week\\[3pt]
Green beans & 20 & 3–4 beans, choped fine & Safe fiber\\[3pt]
Sweet potato & 20 & 1 tbsp mash & Slow carbs\\[3pt]
Pumpkin & 20 & 2 tbsp mash & Gut motility\\[3pt]
Banana (fruit) & 15 & 2–3 slices & Occasional dessert/treat --- Max once per week\\[3pt]
\bottomrule
\end{tabularx}

\vspace{2mm}

\begin{flushleft}
\textbf{Feeding Notes}\\[2pt]
Pick any one vegetable per meal. Use rotation across meals to avoid monotony. 
All vegetables are boiled or lightly steamed, unseasoned, and unsalted.
Avoid onions, garlic, broccoli, cauliflower, or starchy fillers. 
Keep total vegetable content near 20g/meal or as noted. 
\end{flushleft}

\vspace{0.5mm}

\begin{flushleft}
\textbf{Growlrr Dairy \& Carbohydrate Advisory — EU / US (Oats + Greek yogurt option)}\\[4pt]
This adaptation is the Growlrr equivalent of the Indian \emph{curd + rice} staple, tailored for EU / US kitchens where rolled oats and plain cultured Greek yogurt are more common. 
The objective is identical: provide readily accessible, digestible carbohydrates and live probiotic cultures in addition to Growlrr's protein and nutrient dense packs. 
\end{flushleft}

\vspace{0.5mm}

\begin{table}[h]
\centering
\caption{EU/US Dairy \& Carbohydrate Options}
\label{tab:eu_us_dairy}
\begin{tabularx}{\linewidth}{@{} p{3cm} p{2.5cm} X @{}}
\toprule
\textbf{Component} & \textbf{Qty per meal} & \textbf{Guidance and Notes} \\
\midrule
Rolled oats & 150 g (or ½ cup) & Cook rolled oats until soft; mix with yogurt while warm\\[4pt]
Unsweetened Greek yogurt (live cultures) & 100 g &
Preferred EU/US substitute for full curd. Must be \textbf{unsweetened, plain, full-fat}, and labelled \emph{``live active cultures''} (or equivalent). Greek yogurt is often strained; if texture is extremely thick, add 20--30 ml unsalted buttermilk or water to reach spoonable consistency for mixing.\\[4pt]
Cultured buttermilk / kefir (backup) & 100 ml &
Cultured buttermilk or kefir (plain, unsweetened, pasteurised milk origin) are acceptable alternates. Kefir is probiotic-rich but may have stronger flavour; introduce gradually.\\[4pt]
Ricotta / cottage cheese (pasteurised) & 100 g &
Acceptable non-probiotic fallback for short-term when live-culture yogurt is not available. Use plain \textbf{pasteurised} ricotta or low-salt cottage cheese. These supply calcium and proteins but no probiotics.\\[4pt]
Plant-based ``yogurts'' (soy, almond, oat) & --- &
Do \textbf{not} use routinely unless under veterinary guidance. They lack animal-based amino acids and deliver different mineral profiles; their use may require compensatory formulation adjustments.\\[4pt]
Fat correction & --- &
If using low-fat yogurt, add ½ teaspoon unsalted butter or ghee per $\sim$250 g mix to restore energy density for active dogs. This helps match the caloric role of whole-milk curd.\\
\bottomrule
\end{tabularx}
\end{table}

\vspace{0.5mm}

\begin{flushleft}
\textbf{Handling, Safety \& Freshness}\\[2pt]
\begin{itemize}[noitemsep]
  \item Use only \textbf{pasteurised} Greek Yogurt labelled with live cultures for probiotic benefit. Avoid sweetened, flavoured, or fruit-added products.
  \item Store cultured dairy at $\leq$ 4 °C (40 °F). Discard if discolored, odour becomes sour, or if abnormal whey separation occurs (large pools of discoloured liquid).
  \item Boil oats and vegetables together where possible to retain nutrients.
  \item If using Greek yogurt that is highly s
  \item Always introduce dairy gradually if new. Watch for signs of lactose intolerance. Consult our vet at www.growlrr.com if needed.
\end{itemize}
\end{flushleft}








