\documentclass[10pt,a6paper,landscape]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=3mm]{geometry}
\usepackage{multicol}
\usepackage{array}
\usepackage{tabularx}
\usepackage{graphicx}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1mm}

\begin{document}

\begin{multicols}{3}
\setlength{\columnseprule}{0.2pt}

% COLUMN 1 - FRONT PANEL
{\Large\bfseries Growlrr CatCore --- Heart (H) --- 100g}

\vspace{2mm}
{\footnotesize\bfseries Complete \& Balanced Nutrition for Adult Cats - All Life Stages}

{\tiny Feed as part of Growlrr Rotation System for optimal health}

\vspace{3mm}
\hrule
\vspace{1mm}

{\small\bfseries PET NUTRITION FACTS}

{\tiny
\begin{tabular}{|p{3cm}|r|}
\hline
\multicolumn{2}{|c|}{\textbf{Serving Size: 1 pouch (100g)}} \\
\multicolumn{2}{|c|}{\textbf{Calories: 112 kcal}} \\
\hline
\textbf{Nutrient} & \textbf{Guarantee} \\
\hline
Protein (min) & 15.8\% \\
Fat (min) & 5.2\% \\
Total Carb (max) & 4.5\% \\
Dietary Fiber (max) & 0.4\% \\
Moisture (max) & 72\% \\
Omega-3 (min) & 2.5ml \\
\hline
\end{tabular}
}

\vspace{2mm}
{\tiny\bfseries Complete \& Balanced when fed as part of Growlrr Rotation System}

\vspace{3mm}
{\small\bfseries ROTATION FEEDING SYSTEM}

{\tiny
Feed one LIGHT + one DARK pouch daily. Rotate weekly across all six SKUs.

Monday: Heart (red) + Lamb (red)

Tuesday: Liver (blue) + Sardine (blue)

Wednesday: Kidney (brown) + Gizzard (brown)

Why rotate?
\begin{itemize}
\item Mimics natural prey variety
\item Prevents dietary monotony
\item Reduces food sensitivity risk
\item Optimizes micronutrient balance
\end{itemize}

Each pouch is complete on its own. Rotation optimizes long-term vitality.

Free custom diet chart: www.growlrr.com/diet
}

\vspace{3mm}
{\small\bfseries FEEDING GUIDELINES}

{\tiny
\begin{tabular}{ll}
Kittens (<1yr): & 3-4 pouches/day \\
Adult (1-7yr): & 2 pouches/day \\
Senior (7+yr): & 2 pouches/day \\
\end{tabular}

Adjust for activity, metabolism, and body condition. Transition gradually over 7 days.

Always provide fresh water.

For pregnant/nursing cats or medical conditions, consult veterinarian.
}

\columnbreak

% COLUMN 2 - INGREDIENTS & WHY FORTIFY
{\small\bfseries INGREDIENTS (by weight)}

{\tiny
Chicken Bone Broth (41.5g), Chicken Heart (24.0g), Chicken Frame Mince (20.0g), Chicken Muscle Cuts (11.0g), Pumpkin Puree (4.0g), Egg Yolk Powder (4.0g), Chicken Liver (2.0g), Omega-3 Fish Oil (2.5ml)

\textbf{FORTIFICATION (CatPro v5 - 1g):}

Choline Chloride, DL-Methionine, Taurine, Magnesium Oxide, Potassium Citrate, Calcium Pantothenate, Thiamine Mononitrate, Riboflavin, Niacinamide, Pyridoxine HCl, Folic Acid, Biotin, Vitamin B12, Vitamin A Palmitate, Vitamin D3, Vitamin E (Mixed Tocopherols), Zinc Bisglycinate, Iron Proteinate, Copper Proteinate, Manganese Proteinate, Selenium Yeast, Potassium Iodide, Glucosamine HCl, Chondroitin Sulfate, MSM, Cranberry Extract, Fructooligosaccharides (FOS Prebiotics)

\textbf{PRESERVATIVES:} Mixed Tocopherols, Citric Acid, Grape Polyphenols

NO grains | NO fillers | NO BHA/BHT
}

\vspace{3mm}
\hrule
\vspace{1mm}

{\small\bfseries WHY ADD VITAMINS IF MEAT IS COMPLETE?}

{\tiny
Because 65g of meat in a pouch---even premium organs---cannot deliver 100\% of 40+ essential nutrients cats need daily.

Heat processing reduces some vitamins. Raw/homemade diets face the same gap---most lack adequate taurine, calcium, vitamin E, and trace minerals.

\textbf{Our promise: radical transparency.} Every ingredient listed. Every nutrient quantified. What you see is what you get---no hidden fillers, no ambiguous 'natural flavors.' Just honest nutrition.
}

\vspace{3mm}
\hrule
\vspace{1mm}

{\small\bfseries YOUR QUESTIONS ANSWERED}

{\tiny
\textbf{Q: Why so many chemical names?}

A: Because transparency requires precision. "Natural flavor" could mean anything. "Choline chloride" tells you exactly what's inside.

\textbf{Q: Can't meat provide everything?}

A: No. Wild cats eat whole prey---bones, organs, fur, stomach contents. A pouch can't fit a whole mouse. Fortification replicates prey nutrition.

\textbf{Q: Is this 'processed'?}

A: Retort sterilization (like home canning) preserves food safely. Premixes are measured nutrients, not mystery powders.

\textbf{Q: Why not just raw?}

A: Raw feeders use supplements too---ours are just pre-mixed and lab-verified for safety.
}

\columnbreak

% COLUMN 3 - FUNCTIONAL BENEFITS & FOOTER
{\small\bfseries WHAT'S WORKING FOR YOUR CAT}

{\tiny
\textbf{JOINT HEALTH}

Glucosamine 50mg, Chondroitin 30mg, MSM 20mg

\textbf{URINARY SUPPORT}

Cranberry Extract, DL-Methionine, Low Sodium, Optimized pH

\textbf{GUT HEALTH}

FOS Prebiotics (feeds good bacteria)

\textbf{VISION \& IMMUNITY}

Taurine 100mg, Vitamin A 500 IU, Zinc 2.3mg, Selenium 11mcg

\textbf{SKIN \& COAT}

Omega-3 Fish Oil 2.5ml, Biotin, B-Complex vitamins

\textbf{DENTAL \& BONE}

Calcium 220mg, Phosphorus 175mg, Optimized Ca:P ratio 1.26:1
}

\vspace{3mm}
\hrule
\vspace{1mm}

{\small\bfseries QUALITY PROMISE}

{\tiny
\begin{itemize}
\item Human-Grade Ingredients
\item Antibiotic-Free Poultry
\item Traceable Sourcing
\item NABL Lab-Tested
\item Low-Temp Cooking preserves nutrients
\end{itemize}

\textbf{Storage:} Room temperature before opening. After opening: Refrigerate, use within 48 hours.

\textbf{Shelf Life:} 18 months. Retort sterilized for safety.

\textbf{Keep Fresh Water Available}

Meets AAFCO/FEDIAF when paired \& rotated
}

\vspace{3mm}
\hrule
\vspace{1mm}

{\tiny
Batch: \_\_\_\_\_\_\_\_\_\_\_ Mfg: \_\_\_\_\_\_\_\_\_\_\_

NOT FOR SALE --- R\&D PILOT ONLY

(c)2025 Growlrr Foods Pvt Ltd

Made in India

www.growlrr.com | hello@growlrr.com

Rev H.3.0.0

[BARCODE SPACE]
}

\end{multicols}

\end{document}