\subsection*{Appendix A1 --- Thiamine (B1) Retort Loss and Overage Policy\cite{ref7}}

\textbf{Background:}  
Thiamine (Vitamin B1) is the most labile water-soluble vitamin in retorted diets. Industry and NRC reports cite losses ranging from 25\% to 90\%, depending on F$_0$, pH, pouch fill, and matrix. Cats are uniquely sensitive to thiamine deficiency; thus, Growlrr adopts a conservative premix strategy.

\textbf{Locked CatPro Spec (canonical):}  
\begin{itemize}[leftmargin=1.2em]
  \item CatPro provides thiamine = \textbf{0.19 g per 10 kg run} = 190 mg / 10 kg.
  \item Batch = 100 pouches $\rightarrow$ 1.90 mg/pouch pre-retort.
  \item AAFCO floor = 1.1 mg / 1000 kcal. With pouch $\approx$ 100 kcal $\rightarrow$ 0.11 mg/pouch required post-retort.
\end{itemize}

\textbf{Retention Scenarios (illustrative):}

\begin{tabular}{lrrr}
\toprule
Assumed Retort Loss & Post-retort (mg/pouch) & Post-retort (mg/1000 kcal) & Margin vs AAFCO floor \\
\midrule
25\% loss & 1.43 & 14.3 & +1200\% \\
40\% loss & 1.14 & 11.4 & +936\% \\
80\% loss & 0.38 & 3.8 & +245\% \\
90\% loss & 0.19 & 1.9 & +73\% \\
\bottomrule
\end{tabular}

\textbf{Interpretation:}  
Even under catastrophic 90\% loss, Growlrr CatPro delivers \textgreater 70\% margin over AAFCO minima. At realistic 25--40\% losses, retention is 8--12$\times$ above floor. This strategy eliminates risk of deficiency while avoiding unnecessary megadoses.

\textbf{Policy (canonical, frozen):}
\begin{enumerate}[leftmargin=1.2em]
  \item CatPro thiamine premix is fixed at 0.19 g/10 kg run (1.9 mg/pouch pre-retort).  
  \item Compliance assumption: 40\% conservative loss.  
  \item QC: Pilot assays must confirm $\geq$60\% retention. If lower, adjust process or premix under change-control.  
  \item Internal review trigger: if lane-normalised thiamine falls below 2 mg/1000 kcal post-retort.  
\end{enumerate}

\textbf{Why this matters:}  
- Prevents deficiency in cats (neurologic signs, anorexia, death in weeks if untreated).  
- Safe overages: B1 is water-soluble, with no practical toxicity.  
- Aligns with AAFCO/FEDIAF/NRC guidance, provides optics of robustness, and ensures audit resilience.

\textbf{SOP insertion (batch record):}
\begin{itemize}[leftmargin=1.2em]
  \item Verify premix COA for thiamine mg/kg.  
  \item Confirm dosing = 100 g premix per 10 kg run.  
  \item Record expected pre-retort and post-retort values in run sheet.  
  \item Compare finished-product assay to design assumptions; log variance.  
\end{itemize}
