\subsection*{Appendix B3 --- Choline Buffer Strategy}

\textbf{Background:}  
Choline is essential for membrane phospholipids, acetylcholine neurotransmission, and methyl group metabolism. Cats cannot synthesize enough endogenously; dogs also have dietary requirement. Deficiency leads to hepatic lipidosis, poor growth, neurologic signs.  

\textbf{AAFCO/FEDIAF Floors:}  
- Cat minimum: 600 mg / 1000 kcal (as-fed).  
- Dog minimum: 1360 mg / 1000 kcal (as-fed).  
- No explicit ceiling.  

\textbf{Locked Premix Baseline (CatPro v4.2, DogPro v4.1):}  
\begin{itemize}[leftmargin=1.2em]
  \item Choline chloride 60\%: 28 g / 100 g premix cut.  
  \item Dosed at 100 g / 10 kg line (1 g/pouch).  
  \item Provides \textbf{~280 mg choline / pouch} = ~2800 mg / 1000 kcal (assuming 100 kcal/pouch).  
\end{itemize}

\textbf{Natural Organ Contribution:}  
- Egg yolk: ~294 mg/100 g $\rightarrow$ ~24 mg per 8 g inclusion.  
- Heart \& gizzard: minor contribution (~10--15 mg/pouch).  
- Net = ~40 mg additional/pouch.  

\textbf{Compliance Statement:}  
- Premix baseline alone exceeds AAFCO/FEDIAF floors for both cats \& dogs ($\geq$2800 vs 600--1360 mg / 1000 kcal).  
- Natural foods add buffer, but not relied on for baseline compliance.  
- No ceiling risk: wide safety margin, studies show >7500 mg/1000 kcal tolerated without adverse effects.  

\textbf{SOP note:}  
- Verify COA of choline chloride 60\% per cut.  
- Confirm batch dosing 100 g premix/10 kg run.  
- Run label claim per 1000 kcal = 2800 mg.  

