\subsection*{Appendix B4 --- Taurine Buffer Strategy}

\textbf{Background:}  
Taurine is an essential $\beta$-amino acid for cats (bile acid conjugation, myocardium, retina). Dogs synthesize some taurine but certain breeds are predisposed to deficiency (e.g., retrievers). Deficiency = feline dilated cardiomyopathy, retinal degeneration.  

\textbf{AAFCO/FEDIAF Floors:}  
- Cats: 1000 mg / 1000 kcal (canned food).  
- Dogs: no formal minimum, but supplementation is considered best practice for safety.  

\textbf{Locked Premix Baseline (CatPro v4.2, DogPro v4.1):}  
\begin{itemize}[leftmargin=1.2em]
  \item Taurine included: 5 g / 100 g premix cut.  
  \item At 100 g premix / 10 kg run = 1 g/pouch.  
  \item \textbf{100 mg taurine / pouch} = ~1000 mg / 1000 kcal baseline.  
\end{itemize}

\textbf{Natural Organ Contribution:}  
- Heart: ~600 mg/100 g $\rightarrow$ ~200 mg per 32 g inclusion.  
- Gizzard: ~170 mg/100 g $\rightarrow$ ~40 mg per 22 g inclusion.  
- Liver \& kidney: minor (~10--15 mg each/pouch).  
- Combined = ~250--300 mg taurine/pouch = ~2500--3000 mg/1000 kcal natural.  

\textbf{Compliance Statement:}  
- Baseline premix ensures floor (1000 mg/1000 kcal) is always met.  
- Organs provide abundant buffer, often doubling/tripling floor values.  
- No ceiling risk: taurine has no known toxicity in cats or dogs at dietary levels.  

\textbf{SOP note:}  
- Verify taurine concentration per COA in premix batch.  
- Maintain conservative overage to offset ~10\% retort loss.  
- Document natural contribution separately in QC log.  

