\subsection*{Appendix B7 --- Selenium, Zinc, and Iron Strategy}

\textbf{Background:}  
These three minerals are critical for enzyme systems, antioxidant defense, and oxygen transport.  
- Selenium is uniquely narrow in safe range.  
- Zinc interacts with copper/manganese and is essential for skin, coat, and immune function.  
- Iron is vital for hemoglobin and energy metabolism but can accumulate if oversupplied.  

\textbf{Regulatory Standards (AAFCO/FEDIAF, per 1000 kcal):}  
\begin{itemize}[leftmargin=1.2em]
  \item Selenium: floor 0.09 mg; ceiling 0.45 mg  
  \item Zinc: floor 18.5 mg; ceiling 2000 mg  
  \item Iron: floor 7.5 mg; no defined ceiling (toxicity >500 mg/1000 kcal in literature)  
\end{itemize}

\textbf{Locked Premix Baseline (per pouch, via CatPro/DogPro @1 g/pouch):}  
\begin{itemize}[leftmargin=1.2em]
  \item Selenium: 0.001 g / 100 g premix $\rightarrow$ $\sim$0.10 mg/pouch (1000 kcal basis: $\sim$0.12 mg)  
  \item Zinc: 0.225 g / 100 g premix $\rightarrow$ $\sim$20 mg/pouch (per 1000 kcal basis: $\sim$20--21 mg)  
  \item Iron: 0.150 g / 100 g premix $\rightarrow$ $\sim$9 mg/pouch (per 1000 kcal basis: $\sim$9 mg)  
\end{itemize}

\textbf{Natural Ingredient Contribution (per pouch, literature values):}  
\begin{itemize}[leftmargin=1.2em]
  \item Selenium: Egg yolk (25--30 $\mu$g/egg), sardine (0.4--0.6 $\mu$g/g), kidney/liver small traces. Adds $\sim$0.02--0.05 mg/pouch.  
  \item Zinc: Meat/organs (2--5 mg/100 g), sardine (1--2 mg/100 g). Adds $\sim$1--2 mg/pouch.  
  \item Iron: Liver rich (6--8 mg/100 g), kidney (4--6 mg/100 g), heart (3--4 mg/100 g). Adds $\sim$1.5--3 mg/pouch depending on SKU.  
\end{itemize}

\textbf{Post-Retort Loss Assumptions:}  
- Selenium (organic yeast form stable, negligible loss).  
- Zinc \& iron stable under retort.  
$\rightarrow$ No additional overages required beyond premix.  

\textbf{Compliance Statement:}  
- Selenium: With premix $\sim$0.12 mg/1000 kcal + food $\sim$0.03 mg $\rightarrow$ total $\sim$0.15 mg/1000 kcal. Safely above 0.09 mg floor, <30\% of 0.45 mg ceiling.  
- Zinc: $\sim$20--22 mg/1000 kcal, just above 18.5 mg floor, <2\% of ceiling.  
- Iron: $\sim$10--12 mg/1000 kcal, above floor, far below any tox risk.  

\textbf{SOP Notes:}  
\begin{enumerate}[leftmargin=1.2em]
  \item Selenium source: selenium yeast preferred (organic form $\rightarrow$ higher bioavailability, safety). Inorganic sodium selenite avoided.  
  \item Routine premix COA verification: Se, Zn, Fe declared values must match dosing spec.  
  \item No additional Zn/Fe fortification permitted beyond premix.  
  \item Liver inclusion controlled ($\leq$5 g in any SKU) to avoid Fe spikes.  
\end{enumerate}

\textbf{Outcome:}  
This trinity is fully buffered by premix and natural meats:  
- Selenium = green (narrow but controlled).  
- Zinc = green (just above floor, no excess).  
- Iron = green (organ contribution balanced by rotation).
