%------------------------------------------------------------
% Growlrr Foods --- Gel / Alg-Um Premix --- Rev 3.0.0
%------------------------------------------------------------
\subsection*{Gel / Alginate-Encapsulated Calcium Premix (100 g packet)}
\addcontentsline{toc}{subsection}{Gel / Alginate-Encapsulated Calcium Premix (100 g packet)}

\begin{table}[h]
\caption{Gel / Alginate-Calcium Premix Composition (per 100 g premix)}
\label{tab:alginate_gel}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Remarks} \\
\midrule
Sodium alginate & 60.000000 & High-viscosity grade (200--300 cP @ 1\%) \\
Encapsulated Ca-lactate catalyst & 39.5000000 & High melting heat triggered polymeric microgranular encapsulation; Reliable Ca trigger for gelation \\
Anti-caking carrier (carrier q.s) & 0.5000000 & q.s carrier \\
\midrule
\textbf{Total} & \textbf{100.000000 g} & \textbf{Use 1 packet per 10 kg run (1 g / pouch); MOQ Premix 1 kg individually packed into 100 g packets} \\
\bottomrule
\end{tabular}
\end{table}
\vspace{0.5em}

% LaTeX fragment — Encapsulated Calcium Lactate specification (drop-in)
\textit{Encapsulated Calcium Lactate — Vendor Specification}

\begin{itemize}
  \item \textbf{Active:} Calcium lactate (encapsulated) — \textit{elemental Ca 20\,\% w/w nominal.}
  \item \textbf{Physical form:} free-flowing microgranules; target particle-size D50 \(\leq\) 300\,µm; no fragments \(>\)1\,mm.
  \item \textbf{Coating:} food-grade high-melting lipid or heat-triggered polymeric coat; no low-melt coatings that release at \(\leq\)45\,\(^\circ\)C.
  \item \textbf{Release profile (validated):}
    \begin{itemize}
      \item \(\leq\)10\% release (w/w active) after 30\,min at 45\,\(^\circ\)C in aqueous broth under standard agitation.
      \item \(\geq\)80\% release (w/w active) after full retort cycle (e.g. 121\,\(^\circ\)C, process-specific hold time) — vendor to provide thermal-release validation that matches our retort cycle.
    \end{itemize}
  \item \textbf{Solubility / behavior:} core salt (calcium lactate) is water-soluble when unencapsulated; encapsulate must remain intact in mix/fill conditions and release under retort thermal/pressure profile.
  \item \textbf{Taste / organoleptic:} coated granules produce \textit{no detectable} metallic/alkaline off-flavour at the intended inclusion (acceptance by sensory panel required).
  \item \textbf{Stability:} shelf-stable at ambient (≤30\,\(^\circ\)C) for \(\geq\)12 months; no migration or leaching of core under storage (vendor stability data required).
  \item \textbf{Heat/Retort compatibility:} coating must not soften and bleed during pre-retort hold or during processing prior to fill; vendor to certify retort survivability and release curve.
  \item \textbf{Microbiological:} total plate count and yeast/mould within vendor spec; free of pathogens; supply certificate of analysis (CoA) with each lot.
  \item \textbf{Labeling:} declare as ``Calcium (as encapsulated calcium lactate premix)''; provide elemental Ca per g premix on CoA.
  \item \textbf{QC tests (supplier deliverables):}
    \begin{enumerate}
      \item Particle-size distribution (laser/D50) report.
      \item Thermal-release study (45\,\(^\circ\)C hold and retort equivalent) with % release vs time curve.
      \item Elemental Ca assay (ICP) confirming 20\% ±2\%.
      \item Sensory release check post-retort (3 replicate pouches).
    \end{enumerate}
\end{itemize}


