% ---------------------------------------------------------------------
% Growlrr Foods -- CatPro v5 COA / Incoming QC Checklist (100 g packet)
% Rev H.3.0.3 - Updated formulation values with CAS numbers
% ---------------------------------------------------------------------
\subsection*{COA and Incoming QC - CatPro v5 (100 g packet) with RED Sticker}
\addcontentsline{toc}{subsection}{COA and Incoming QC - CatPro v5}
\noindent\textit{All weights are expressed in grams (g) per 100 g premix formulation. Carrier (q.s.) to reach 100 g}
\begin{longtable}{@{}p{6.0cm}p{1.5cm}p{1.8cm}p{2.0cm}p{3.0cm}p{3.0cm}@{}}
\caption{Catpro Premix Composition COA and Incoming QC (per 100 g premix)}\\
\toprule
\textbf{Parameter} & \textbf{Unit} & \textbf{Spec} & \textbf{CAS No.} & \textbf{Method / Instrument} & \textbf{Result / Comments} \\
\midrule
\endfirsthead
\toprule
\textbf{Parameter} & \textbf{Unit} & \textbf{Spec} & \textbf{CAS No.} & \textbf{Method / Instrument} & \textbf{Result / Comments} \\
\midrule
\endhead

\multicolumn{6}{l}{\textbf{Identification and Batch}} \\[3pt]
Product name or code & --- & CatPro v5 (100 g packet) & --- & Visual label check & \\[3pt]
Color Coded RED Sticker & --- & Red & --- & Visual & \\[3pt]
Lot or Batch number & --- & Supplier lot number present & --- & Visual & \\[3pt]
Manufacture date & --- & Present & --- & Visual & \\[3pt]
Expiry or Best before & --- & Present & --- & Visual & \\[6pt]

\multicolumn{6}{l}{\textbf{Physical and Packaging}} \\[3pt]
Net packet mass & g & 100.00 +/- 0.20 & --- & Analytical balance (tare) & \\[3pt]
Appearance & --- & Free flowing, no caking, no oil separation & --- & Visual inspection & \\[3pt]
Odour & --- & Characteristic, not rancid or off odour & --- & Sensory & \\[3pt]
Color & --- & Off white to pale beige & --- & Visual & \\[3pt]
Particle size (D90) & um & <= 250 & --- & Sieve or laser diffraction & \\[3pt]
Bulk density & g mL$^{-1}$ & 0.40 to 0.65 & --- & Volumetric fill test & \\[3pt]
Moisture (loss on drying) & \% w/w & <= 4.0 & --- & AOAC 925.10 (LOD) & \\[6pt]

\multicolumn{6}{l}{\textbf{Composition (assay) - key actives per 100 g packet}}  \\[3pt]
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Assay/Grade} & \textbf{Tolerance $\pm$ (g)} & \textbf{CAS Number} & \textbf{Supplier Specification} \\
\midrule
Choline chloride & 32.000 & 60\% assay & 0.500 & 67-48-1 & USP/FCC grade; free-flowing powder \\[3pt]
Taurine & 15.000 & $\ge$98.5\% purity & 0.200 & 107-35-7 & USP grade; pharmaceutical quality \\[3pt]
Magnesium gluconate & 10.000 & USP grade & 0.100 & 3632-91-5 & Dihydrate form; food grade \\[3pt]
L-Carnitine tartrate & 9.000 & $\ge$98\% L-carnitine & 0.100 & 36687-82-8 & 2:1 L-carnitine:tartrate ratio \\[3pt]
Inulin (chicory root) & 8.000 & FOS $\ge$90\% & 0.100 & 9005-80-5 & Prebiotic fiber; food grade \\[3pt]
Betaine (TMG) & 6.000 & $\ge$98\% purity & 0.100 & 107-43-7 & Anhydrous; food grade \\[3pt]
Potassium citrate & 5.000 & Tripotassium citrate food grade & 0.050 & 866-84-2 & Monohydrate; USP/FCC \\[3pt]
DL-Methionine & 3.500 & USP grade $\ge$98.5\% & 0.050 & 59-51-8 & Free amino acid form \\[3pt]
Ascorbic acid & 2.000 & $\ge$99\% purity & 0.050 & 50-81-7 & Fine powder; USP grade \\[3pt]
Vitamin K$_2$ (MK-7) & 1.700 & 1.0\% menaquinone-7 assay & 0.050 & 2124-57-4 & Spray-dried on carrier; $\ge$1.0\% MK-7 \\[3pt]
L-Cysteine & 1.500 & USP grade $\ge$98\% & 0.050 & 52-90-4 & Free base or HCl form \\[3pt]
Zinc bisglycinate chelate & 1.100 & 25\% elemental Zn & 0.050 & 14281-83-5 & Chelated form; GRAS \\[3pt]
Calcium pantothenate & 0.800 & $\ge$98\% B$_5$ & 0.050 & 137-08-6 & D-form; USP grade \\[3pt]
Iron proteinate & 0.750 & 20\% elemental Fe & 0.050 & 9007-73-2 & Chelated organic form \\[3pt]
Selenium yeast & 0.550 & 0.20\% elemental Se & 0.050 & Various & Organic selenium; food grade \\[3pt]
Copper proteinate & 0.300 & 10\% elemental Cu & 0.030 & 9007-73-2 & Chelated organic form \\[3pt]
Niacin (B$_3$) & 0.250 & $\ge$99\% purity & 0.020 & 59-67-6 & Nicotinic acid or niacinamide \\[3pt]
Thiamine HCl (B$_1$) & 0.190 & $\ge$99\% purity & 0.020 & 67-03-8 & Hydrochloride form; USP \\[3pt]
Manganese proteinate & 0.150 & 10\% elemental Mn & 0.020 & 9007-73-2 & Chelated organic form \\[3pt]
Riboflavin (B$_2$) & 0.050 & $\ge$98\% purity & 0.010 & 83-88-5 & USP grade; fine powder \\[3pt]
Pyridoxine HCl (B$_6$) & 0.050 & $\ge$98\% purity & 0.010 & 58-56-0 & Hydrochloride form; USP \\[3pt]
Vitamin D$_3$ & 0.035 & 100000 IU/g cholecalciferol & 0.005 & 67-97-0 & Spray-dried; stabilized \\[3pt]
Vitamin A palmitate & 0.015 & 320000 IU/g retinyl palmitate & 0.005 & 79-81-2 & Spray-dried; stabilized \\[3pt]
Potassium iodate & 0.010 & $\ge$99.5\% KIO$_3$ & 0.002 & 7758-05-6 & Food grade; iodine source \\[3pt]
D-Biotin (B$_7$) & 0.008 & $\ge$98\% purity & 0.002 & 58-85-5 & Pharmaceutical grade; pure crystalline \\[3pt]
\midrule
Mixed tocopherols ( 50\% active) & 1.000 &  & 0.050 & (($\alpha:\beta:\gamma:\delta$) =1.0:0.3:6.0:2.0) &  GRAS stabilizer \\[3pt]
\midrule

\multicolumn{6}{l}{\textbf{Microbiology}} \\[3pt]
Total aerobic plate count (TPC) & cfu g$^{-1}$ & <= 1e4 & --- & ISO 4833 Plate count & \\[3pt]
Yeast and mould & cfu g$^{-1}$ & <= 1e3 & --- & ISO 21527 Plate count & \\[3pt]
Salmonella spp. & per 25 g & Not detected & --- & ISO 6579 Enrichment & \\[3pt]
Enterobacteriaceae & cfu g$^{-1}$ & <= 1e3 & --- & ISO 21528 & \\[6pt]

\multicolumn{6}{l}{\textbf{Contaminants and Safety}} \\[3pt]
Heavy metals (Pb) & mg kg$^{-1}$ & <= 0.5 & 7439-92-1 & ICP MS & \\[3pt]
Heavy metals (Cd) & mg kg$^{-1}$ & <= 0.2 & 7440-43-9 & ICP MS & \\[3pt]
Aflatoxin (total) & ug kg$^{-1}$ & <= 10 & Various & LC MS MS & \\[3pt]
Melamine & mg kg$^{-1}$ & Not detected or Below LOQ & 108-78-1 & LC MS MS & \\[6pt]

\multicolumn{6}{l}{\textbf{Physical and Stability}} \\[3pt]
Bulk water activity (a$_w$) & --- & <= 0.60 & --- & Aqualab or Rotronic & \\[3pt]
Peroxide value (if oil included) & meq O$_2$ kg$^{-1}$ & <= 5.0 & --- & AOCS Cd 8b 90 & NA for dry premix \\[6pt]

\multicolumn{6}{l}{\textbf{Packaging and Storage}} \\[3pt]
Packet seal integrity & --- & No leaks, hermetic seal & --- & Vacuum or visual & \\[3pt]
Pouch labelling & --- & Lot, Mfg date, Expiry, COA & --- & Visual & \\[3pt]
Storage conditions & --- & Store dry, 10 to 20 C, RH < 60\% & --- & Visual or log & \\[6pt]

\multicolumn{6}{l}{\textbf{Acceptance}} \\[3pt]
Sample size for incoming QC & --- & 1 packet per 10 boxes or ISO sampling plan & --- & QA plan & \\[3pt]
Release decision & --- & Accept or Reject or Hold & --- & QA manager signature & \\[6pt]

\multicolumn{6}{l}{\textbf{Sign off}} \\[3pt]
Checked by (incoming QC) & Name or Sign & Date & --- & Comments & \\[12pt]
Approved by (QA Manager) & Name or Sign & Date & --- & Comments & \\
\bottomrule
\end{longtable}
\vspace{1em}
% ------------------- NOTES -------------------
\vspace{1em}

\subsection*{Composition for CatCorePro}

\begin{table}[h]
\centering
\caption{CatCorePro Composition per 10 kg run (or 100 pouches)}
\label{tab catcorepro_composition}
\begin{tabular}{@{}l r r@{}}
\toprule
\textbf{Component} & \textbf{Dose per 10 kg} & \textbf{Per pouch} \\
\midrule
CatCore Fresh Meat Protiens & 6500g & 65g \\ [3pt]
Omega-3 Fish Oil PV<=5.0meq/Kg & 250ml & 2.50ml \\[3pt]
CatPro Premix & 100 g & 1.0 g \\[3pt]
Mixed tocopherol liquid premix & 100 ml & 1.0 ml \\[3pt]
Palatant Liquid Premix & 100ml & 1.0ml \\[3pt]
Alginate gel - Ca Premix & 100g & 1.0g \\[3pt]
\midrule
Rendered Bone Broth & 4150g & 41.5g  \\[3pt]
\midrule
Nett Weight per pouch & 112.5g pre-retort & 101.5g $\pm$0.50; declared weight 100.00g\\[3pt]
\bottomrule
\end{tabular}
\end{table}

\noindent\textbf{Composition Notes:}
\begin{itemize}
\item\itembf {CatCore: }Provides high quality muscle, organ, skeletal and fish meat protiens. Primary source of protiens, fats, vitamins, minerals. 
\item \textbf{Catcore Useage: }6.5 Kg Fresh meat blends per 10 kg production run of CatCore or 65.0 g per 100 g wet food pouch.
\item \textbf{CatPro Premix: } Complements CatCore Protein-Ca Premix with complete essential vitamins, minerals and chelators and adequate retort loss overage. 
\item\textbf{AAFCO Compliance: } Together CatCore and CatPro meets AAFCO requirements for complete and balanced nutrition when paired per diet chart. 
\item\textbf{Design Overages: }Enhanced taurine formulation for cardiac health support. Vitamin A is balanced carefully with daily 4.0g fresh liver from 2 CatCore pouches to avoid stacking. Ca:P >=1.1:1 within AAFCO recommended limits when paired as per diet chart. 
\item \textbf{Antioxidant Premix: } Provides Primary Vitamin E (dl-$\alpha$tocopheryl) and mixed antioxidants for enhanced oxidative stability.
\item \textbf{Alginate Gel - Ca Premix:} Alginate gel forms cross-link chain with Calcium under retort heat. Source of 80mg dietary calcium per 100g wet food. Maintains Ca:P ratio. 
\item \textbf{Omega-3 Fish Oil Blend:} Provides functional Omega-3:Omega-6 fatty acids balance. 
\item \textbf{Palatant Premix: } Meat Hydrolysants for palatability.
\item \textbf{Rendered Bone Broth: } Solvent base for retort processing; improves hydration, adds collagen, chondoitin and other bone joint stability nutrients. 
\item\textbf {Low Sodium:} Sodium Alginate Gel provides $\approx$ 65 mg Na per 100g wet food. Palatant Premix provides additional 47.0mg Na to meet electrolyte balance requirements ($\approx$ 0.15\% Na w/w) as per AAFCO. 
\end{itemize}

