% ---------------------------------------------------------------------
% Growlrr Foods -- DogCore Protein Base COA / Incoming QC (65 g protein solids)
% Rev H.3.0.1 - 6-column CSV format with CAS numbers
% ---------------------------------------------------------------------

\subsection*{COA and Incoming QC - DogCore Protein Base (6500 g solids per Sealed Packet) with YELLOW Sticker}
\addcontentsline{toc}{subsection}{COA and Incoming QC - DogCore Protein Base}
\noindent\textit{All weights are expressed in grams (g)}
\begin{longtable}{@{}p{6.0cm}p{1.5cm}p{1.8cm}p{2.0cm}p{3.0cm}p{3.0cm}@{}}
\caption{DogCore Protein Base COA and Incoming QC (per 100 g wet food pouch)}\\
\toprule
\textbf{Parameter} & \textbf{Unit} & \textbf{Spec} & \textbf{CAS No.} & \textbf{Method / Instrument} & \textbf{Result / Comments} \\
\midrule
\endfirsthead
\toprule
\textbf{Parameter} & \textbf{Unit} & \textbf{Spec} & \textbf{CAS No.} & \textbf{Method / Instrument} & \textbf{Result / Comments} \\
\midrule
\endhead

\multicolumn{6}{l}{\textbf{Identification and Batch}} \\[3pt]
Product name or code & --- & DogCore Protein Base (6500 g) & --- & Visual label check & \\[3pt]
Color Coded YELLOW Sticker & --- & Yellow & --- & Visual & \\[3pt]
Lot or Batch number & --- & Supplier lot present & --- & Visual & \\[3pt]
Manufacture date & --- & Present & --- & Visual & \\[3pt]
Expiry or Best before & --- & Present & --- & Visual & \\[6pt]

\multicolumn{6}{l}{\textbf{Physical and Packaging}} \\[3pt]
Net solids mass per pouch & g & 6500.00 $\pm$ 0.50 & --- & Analytical balance & \\[3pt]
Appearance & --- & Fine powder blend, free-flowing & --- & Visual inspection & \\[3pt]
Odour & --- & Characteristic protein, no rancidity & --- & Sensory & \\[3pt]
Color & --- & Off-white to cream & --- & Visual & \\[3pt]
Particle size (D90) & $\mu$m & $\le$ 300 & --- & Sieve or laser diffraction & \\[3pt]
Bulk density & g mL$^{-1}$ & 0.35 to 0.60 & --- & Volumetric fill test & \\[3pt]
Moisture (LOD) & \% w/w & $\le$ 5.0 & --- & AOAC 925.10 (LOD) & \\[6pt]

\multicolumn{6}{l}{\textbf{Composition per 6500g (assay)}} \\[3pt]
\textbf{Component} & \textbf{Quantity (g)} & \textbf{Assay/Grade} & \textbf{Tolerance $\pm$ (g)} & \textbf{CAS Number} & \textbf{Supplier Specification} \\
\midrule
Whey protein concentrate & 3000.000 & $\ge$80\% protein (WPC80) & 0.500 & 92129-90-3 & Food grade; instantized; low lactose \\[3pt]
Egg white powder & 2200.000 & $\ge$80\% protein & 0.500 & 8001-57-6 & Spray-dried; food grade; pasteurized \\[3pt]
Soy protein isolate & 400.000 & $\ge$90\% protein & 0.200 & 9010-10-0 & Non-GMO preferred; food grade \\[3pt]
Egg yolk powder & 400.000 & Food grade & 0.200 & 8001-57-6 & Spray-dried; high choline content \\[3pt]
Lecithin & 250.000 & $\ge$95\% phospholipids & 0.200 & 8002-43-5 & Soy or sunflower; food grade emulsifier \\[3pt]
Calcium lactate (non-encapsulated) & 200.000 & 20\% elemental Ca & 0.100 & 814-80-2 & Food grade; provides $\approx$400mg Ca per pouch \\[3pt]
Sodium Chloride (NaCl) & 3.5 & $\ge$99.5\% food grade & 0.005 & 7647-14-5 & Common salt; dietary sodium; electrolyte balance \\[3pt]
\midrule
\midrule
Mixed tocopherols ( 50\% active) & 30.00 &  & 0.050 & (($\alpha:\beta:\gamma:\delta$) =1.0:0.3:6.0:2.0) &  GRAS stabilizer \\[3pt]
Anti-caking carrier (q.s.) & 16.5 & Food grade & 0.100 & Various & Silicon dioxide , Maltodextrin; GRAS; flow aid; q.s. to 100.000g \\[3pt]

\multicolumn{6}{l}{\textbf{Protein Quality Parameters}} \\[3pt]
Total crude protein (Nx6.25) & \% w/w & $\ge$ 65.0 & --- & Kjeldahl or Combustion & On dry basis \\[3pt]
Fat content & \% w/w & 8.0 to 12.0 & --- & Soxhlet or NMR & \\[3pt]
Ash content & \% w/w & $\le$ 8.0 & --- & AOAC 942.05 & \\[3pt]
Calcium (total) & mg / 100 g & 400 $\pm$ 50 & --- & ICP OES & Primary from Ca-lactate \\[3pt]
Phosphorus (total) & mg / 100 g & 400 to 600 & --- & ICP OES & From protein sources \\[6pt]

\multicolumn{6}{l}{\textbf{Functional Properties}} \\[3pt]
Solubility in water & \% & $\ge$ 90 & --- & Centrifuge method & At pH 6.8, 20°C \\[3pt]
Emulsification capacity & --- & Good & --- & Visual/functional test & Stable emulsion formation \\[3pt]
Gel strength (post-retort) & --- & Moderate & --- & Texture analyzer & Slurry consistency target \\[6pt]

\multicolumn{6}{l}{\textbf{Microbiology}} \\[3pt]
Total aerobic plate count (TPC) & cfu g$^{-1}$ & $\le$ 5 $\times$ 10$^4$ & --- & ISO 4833 Plate count & \\[3pt]
Yeast and mould & cfu g$^{-1}$ & $\le$ 1 $\times$ 10$^3$ & --- & ISO 21527 Plate count & \\[3pt]
Salmonella spp. & per 25 g & Not detected & --- & ISO 6579 Enrichment & \\[3pt]
Enterobacteriaceae & cfu g$^{-1}$ & $\le$ 1 $\times$ 10$^3$ & --- & ISO 21528 & \\[3pt]
E. coli & cfu g$^{-1}$ & $\le$ 10 & --- & ISO 16649 & \\[6pt]

\multicolumn{6}{l}{\textbf{Contaminants and Safety}} \\[3pt]
Heavy metals (Pb) & mg kg$^{-1}$ & $\le$ 0.5 & 7439-92-1 & ICP MS & \\[3pt]
Heavy metals (Cd) & mg kg$^{-1}$ & $\le$ 0.2 & 7440-43-9 & ICP MS & \\[3pt]
Aflatoxin (total) & $\mu$g kg$^{-1}$ & $\le$ 10 & Various & LC-MS/MS & \\[3pt]
Melamine & mg kg$^{-1}$ & Not detected or Below LOQ & 108-78-1 & LC-MS/MS & \\[6pt]

\multicolumn{6}{l}{\textbf{Allergen Declaration}} \\[3pt]
Milk (whey) & --- & Present (declared allergen) & --- & Label declaration & \\[3pt]
Egg & --- & Present (declared allergen) & --- & Label declaration & \\[3pt]
Soy & --- & Present (declared allergen) & --- & Label declaration & \\[6pt]

\multicolumn{6}{l}{\textbf{Physical and Stability}} \\[3pt]
Bulk water activity (a$_w$) & --- & $\le$ 0.65 & --- & Aqualab or Rotronic & \\[3pt]
Peroxide value & meq O$_2$ kg$^{-1}$ & $\le$ 5.0 & --- & AOCS Cd 8b-90 & For lipid content \\[6pt]

\multicolumn{6}{l}{\textbf{Packaging and Storage}} \\[3pt]
Primary packaging & --- & Food-grade sealed pouches & --- & Visual & Per 6500g pre-weighed \\[3pt]
Secondary packaging & --- & Corrugated box with desiccant & --- & Visual & \\[3pt]
Storage conditions & --- & Store dry, 10--20°C, RH < 60\% & --- & Visual or log & \\[6pt]

\multicolumn{6}{l}{\textbf{Acceptance}} \\[3pt]
Sample size for incoming QC & --- & 1 pouch per 10 boxes & --- & QA plan & \\[3pt]
Release decision & --- & Accept or Reject or Hold & --- & QA manager signature & \\[6pt]

\multicolumn{6}{l}{\textbf{Sign off}} \\[3pt]
Checked by (incoming QC) & Name/Sign & Date & --- & Comments & \\[12pt]
Approved by (QA Manager) & Name/Sign & Date & --- & Comments & \\
\bottomrule
\end{longtable}
\vspace{0.5em}

\begin{table}[h]
\centering
\caption{DogCorePro Composition (per 10 kg run = 100  wet food pouches)}
\label{tab:dogcore_premix}
\begin{tabular}{@{}l r r@{}}
\toprule
\textbf{Component} & \textbf{Dose per 10 kg} & \textbf{Per pouch} \\
\midrule
DogCore Premix (Current spec) & 6500g & 65g \\ [3pt]
\midrule 
DogPro Premix & 100 g & 1.0 g \\[3pt]
Mixed tocopherol liquid Premix & 100 ml & 1.0 ml \\[3pt]
Palatant Liquid Premix & 100ml & 1.0ml \\[3pt]
Omega-3 Fish Oil PV<=5.0meq/Kg & 250ml & 2.50ml \\[3pt]
\midrule
Rendered Bone Broth & 4200ml & 42.0ml \\[3pt]
\midrule
Nett Weight per pouch & 112.5g pre-retort & 101.5g $\pm$0.50; declared weight 100.00g\\[3pt]
\midrule
\bottomrule
\end{tabular}
\end{table}
% ------------------- NOTES -------------------
\vspace{1em}

\subsection*{Composition for DogCorePro}

\noindent\textbf{Composition Notes:}
\begin{itemize}
\item\textbf {DogCore Premix: } Provides high quality protien powders and Calcium to be paired 1:1 with CatCorePro meat pouches.
\item \textbf{DogCore Premix Useage: }6.5 Kg per 10 kg production run of DogCore or 65.0 g per 100 g wet food pouch.
\item \textbf{DogPro Premix: } Complements DogCore Protein-Ca Premix with complete essential vitamins, minerals and chelators and adequate retort loss overage. 
\item\textbf{AAFCO Compliance: } Together DogCore and DogPro meets AAFCO requirements for complete and balanced nutrition when paired with CatCore and CatPro as per diet chart. 
\item\textbf{Design Overages: }Enhanced taurine formulation for cardiac health support. Vitamin A is balanced carefully with daily 4.0g fresh liver from 2 CatCore pouches to avoid stacking. Ca:P >=1.4:1 within AAFCO recommended limits when paired with CatCorePro pouches as per diet chart. 
\item \textbf{Antioxidant Premix: } Provides Primary Vitamin E (dl-$\alpha$tocopheryl) and mixed antioxidants for enhanced oxidative stability.
\item \textbf{Omega-3 Fish Oil Blend:} Provides omega 3:omega 6  balance
\item \textbf{Palatant Premix: } Meat Hydrolyasants for enhanced palatability.
\item\item{Rendered Bone Broth: } Solvent base for retort processing; improves hydration, adds collagen, chondoitin and other bone joint stability nutrients. 
\item \textbf{NO Alginate Gel - Ca Premix:} No alginate gel in this SKU. Forms slurry consistancy. 
\item \textbf{Low Sodium:} DogCore provides $\approx$ 14.0 mg Na per 100g wet food. Palatant Premix provides additional 47.0mg Na to meet electrolyte balance requirements ($\approx$ 0.061\% Na w/w) as per AAFCO when paired with CatCorePro pouches as per diet chart. 
\end{itemize}

