\subsection*{Bill of Materials: CatCore Sardine SKU}
\label{bom:catcore_heart}

\subsubsection*{Batch Specifications}
\begin{itemize}
\item Batch size: 10 kg (100 pouches)
\item Per pouch declared weight: 100 g
\end{itemize}

\subsubsection*{Raw Ingredients}
\begin{table}[h]
\centering
\caption{CatCore Sardine SKU - Raw Materials per 10 kg Batch}
\begin{tabular}{@{}llrrrp{4cm}@{}}
\toprule
\textbf{Ingredient} & \textbf{Per Batch (Kg)} & \textbf{Prep Method}  & \textbf{Traceability Log} & \textbf{Prep Notes} & \textbf{Obs}\\
\midrule
Sardine (whole)     & 5.200 $\pm$0.15  & Cut 1.5cm segments     & [QC-FORM-\_\_\_\_\_\_] & Gutted, cut crosswise & Refrigerate\\
Fish bone meal      & 0.900 $\pm$0.05  & Micronized powder      & [QC-FORM-\_\_\_\_\_\_] & Particle size $\le$150 $\mu$m, pet food grade & Store dry\\
Pumpkin puree       & 0.400 $\pm$0.01  & Blended                & [QC-FORM-\_\_\_\_\_\_] & Washed, blanched and blended into smooth paste & Refridgerate \\
\midrule
\textbf{TOTAL SOLIDS} & \textbf{6.500 $\pm$0.05} & Calibrated Scale & [QC-FORM-\_\_\_\_\_\_] & Maintain Cold Chain Logs & MAINTAIN TIGHT TOLERANCE\\
\bottomrule
\end{tabular}
\end{table}

\subsubsection*{Processing Instructions}
\item Thoroughly wash all meat products in running hot jet stream water for 5 minutes to wash off any blood, coagulants, debris and other undesirable particles. 
\textbf{Solid Preparation (1.5cm Standard):}
\begin{itemize}
\item Measure out each raw ingredient using caliburated scale and tight tolerance. 
\item Use sharp knife or dicer machine
\item All diced ingredients: uniform 1.5cm$\pm$ 0.5cm cubes
\item Maintain strict cold chain logs before, during and after prep (4 deg C)
\item Measure each ingredient post dicing and note down the weight. 
\item Refridgerate immediately before proceeding to next ingredient. 
\item Keep preperation time to under 20 minutes to control pathogen load. 
\end{itemize}

\textbf{Pumpkin Puree Preparation:}
\begin{enumerate}
\item Measure 400g boiled diced pumpkin. 
\item Blend together in hand blender until smooth paste (no lumps)
\item Use within 4 hours or refrigerate overnight (4 deg C; max 12 hours). Maintain coldchain Logs
\item Add to blanched solids during marination process step. Follow SOP30-A
\end{enumerate}



\subsubsection*{Liquid Components}
\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Component} & \textbf{Per Batch (kg)  & \textbf{Per Pouch (g)}} \\
\midrule 
Spring Water &  4.10 $\pm$0.10 & 41.5 \\
Blanch water (process recovery-refer SOP 30-A) & 0.250$\pm$0.010 & 2.5 \\ 
\textbf{TOTAL LIQUIDS} & \textbf {4.350} & {43.5} \textbf \\
\midrule

\bottomrule

\end{tabular}

\vspace{1em}

\begin{itemize}
\item \textbf{CatPro Premix: } Complements CatCore Fresh Proteins with complete essential vitamins, minerals and chelators and adequate retort loss overage.
\item \textbf{Useage:} 100 g per 10 kg production run or 1.0 g per 100 g wet food pouch complements with complete essential vitamins, minerals and chelators. \item\textbf{AAFCO Compliance: } Meets AAFCO requirements for complete and balanced nutrition.
\item\textbf{Design Overages: }Enhanced taurine formulation for cardiac health support. Vitamin A is balanced carefully with daily 4.0g fresh liver from 2 CatCore pouches to avoid stacking.\cite{ref64}.  
\item \textbf{Antioxidant Premix: } 100ml per 10Kg run or 1ml per 100g wet food pouch. Provides Primary Vitamin E (dl-$\alpha$tocopheryl) and blended organic antioxidants for enhanced oxidative stability.
\item \textbf{Alginate Gel - Ca Premix:} 100g per 10Kg run. Forms gel under retort heat. Delivers additional 80mg dietary Ca per 100g wet food pouch.
\item \textbf{Palatant Premix: } 100ml per 10Kg run or 1ml per 100g wet food pouch.
\end{itemize}
